---
title: "2010 Census Data -- Pre-Treatment Baseline"
subtitle: "Saint Lucia Housing Thesis"
author: "Mave Kimara Alexander"
date: today
format:
  pdf:
    toc: true
    number-sections: true
    fig-width: 8
    fig-height: 5
    keep-tex: false
execute:
  warning: false
  message: false
  echo: false
---

```{r}
#| label: setup
#| include: false

library(haven)
library(tidyverse)
library(labelled)
library(kableExtra)
library(scales)
library(ggrepel)

theme_set(
  theme_minimal(base_size = 11) +
  theme(
    plot.title    = element_text(face = "bold", size = 12),
    plot.subtitle = element_text(size = 10, color = "grey40"),
    plot.caption  = element_text(size = 8,  color = "grey55"),
    axis.text     = element_text(size = 9),
    legend.position = "bottom",
    legend.text   = element_text(size = 9)
  )
)

caption_2010 <- "Source: Saint Lucia Population and Housing Census 2010"
```

# Overview

This document presents the district-level housing profile derived from the
2010 Saint Lucia Population and Housing Census. It serves as the
pre-treatment baseline for the difference-in-differences analysis.
All estimates are weighted using the census household weight (HWEIGHT).

The three Castries sub-districts are labelled according to their
official SPSS classifications:

- **Castries City** -- the urban core (District 1)
- **Castries Suburban** -- the peri-urban belt (District 2)
- **Castries Rural** -- the rural hinterland (District 3)

---

# Data Preparation

```{r}
#| label: load-and-build

Raw_Census_Data_2010 <- read_sav("person_house_merged.sav")

Raw_Census_Data_2010 <- Raw_Census_Data_2010 |>
  mutate(household_id_2010 = paste(DISTRICT, ED, HH, sep = "_"))

Thesis_Working_Data_2010 <- Raw_Census_Data_2010 |>
  distinct(household_id_2010, .keep_all = TRUE) |>
  select(
    household_id_2010, DISTRICT, poldist, NPERS,
    H11_TYPE, H13_OWN, H15_WALLS, H16_ROOF, H17_YR_BUILT,
    H18_WATER, H20_TOILET, H21_LIGHTING,
    H23_ROOMS, H24_BEDROOMS, H30_VEHICLES, HWEIGHT
  ) |>
  rename(
    household_id     = household_id_2010,
    district_raw     = DISTRICT,
    constituency     = poldist,
    household_size   = NPERS,
    building_type    = H11_TYPE,
    tenure_status    = H13_OWN,
    wall_material    = H15_WALLS,
    roof_material    = H16_ROOF,
    year_built       = H17_YR_BUILT,
    water_source     = H18_WATER,
    toilet_type      = H20_TOILET,
    lighting_source  = H21_LIGHTING,
    rooms            = H23_ROOMS,
    bedrooms         = H24_BEDROOMS,
    vehicles_owned   = H30_VEHICLES,
    household_weight = HWEIGHT
  ) |>
  zap_labels() |>
  mutate(
    district = case_when(
      district_raw == 1  ~ "Castries City",
      district_raw == 2  ~ "Castries Suburban",
      district_raw == 3  ~ "Castries Rural",
      district_raw == 4  ~ "Anse La Raye",
      district_raw == 5  ~ "Canaries",
      district_raw == 6  ~ "Soufriere",
      district_raw == 7  ~ "Choiseul",
      district_raw == 8  ~ "Laborie",
      district_raw == 9  ~ "Vieux Fort",
      district_raw == 10 ~ "Micoud",
      district_raw == 11 ~ "Dennery",
      district_raw == 12 ~ "Gros Islet",
      TRUE               ~ paste0("Unknown (", district_raw, ")")
    ),
    owner_occupied   = if_else(tenure_status %in% c(1, 2), 1L, 0L),
    long_term_rental = if_else(tenure_status %in% c(3, 4), 1L, 0L),
    across(
      c(household_size, building_type, tenure_status, wall_material,
        roof_material, year_built, water_source, toilet_type,
        lighting_source, rooms, bedrooms, vehicles_owned),
      ~ if_else(. %in% c(-999999999, 999999999), NA_real_, as.numeric(.))
    ),
    piped_water     = if_else(water_source    %in% c(1, 2),    1L, 0L, missing = NA_integer_),
    electricity     = if_else(lighting_source == 1,             1L, 0L, missing = NA_integer_),
    improved_toilet = if_else(toilet_type     %in% c(1, 2, 3), 1L, 0L, missing = NA_integer_),
    durable_walls   = if_else(wall_material   %in% c(1, 2, 3), 1L, 0L, missing = NA_integer_),
    durable_roof    = if_else(roof_material   %in% c(1, 2, 3), 1L, 0L, missing = NA_integer_),
    rooms_clean         = if_else(rooms    > 0, rooms,    NA_real_),
    bedrooms_clean      = if_else(bedrooms > 0, bedrooms, NA_real_),
    persons_per_room    = household_size / rooms_clean,
    persons_per_bedroom = household_size / bedrooms_clean,
    overcrowded         = if_else(persons_per_bedroom > 2, 1L, 0L),
    spare_bedrooms      = bedrooms_clean - household_size,
    hosting_suitable = if_else(
      spare_bedrooms  > 0 &
      piped_water     == 1 &
      electricity     == 1 &
      improved_toilet == 1,
      1L, 0L
    ),
    census_year = 2010L
  ) |>
  filter(!is.na(district))
```

```{r}
#| label: out-hh-count

Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(households = comma(round(sum(household_weight, na.rm = TRUE))),
            .groups = "drop") |>
  arrange(desc(as.numeric(gsub(",", "", households)))) |>
  kbl(col.names = c("District", "Weighted Households"),
      caption   = "Weighted Household Count by District -- 2010") |>
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, position = "center")
```

---

# Rental Supply

```{r}
#| label: rental-supply-calc

Rental_supply_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    long_term_rentals = sum(long_term_rental * household_weight, na.rm = TRUE),
    total_households  = sum(household_weight, na.rm = TRUE),
    rental_share      = long_term_rentals / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(rental_share))
```

```{r}
#| label: out-rental-supply

Rental_supply_2010 |>
  mutate(
    long_term_rentals = comma(round(long_term_rentals)),
    total_households  = comma(round(total_households)),
    rental_share      = percent(rental_share, accuracy = 0.1)
  ) |>
  kbl(col.names = c("District", "Long-Term Rentals", "Total HH", "Rental Share"),
      caption   = "Long-Term Rental Supply by District -- 2010 (Weighted)") |>
  kable_styling(latex_options = c("striped", "hold_position"))
```

```{r}
#| label: fig-rental-supply

Rental_supply_2010 |>
  ggplot(aes(x = reorder(district, rental_share), y = rental_share)) +
  geom_col(fill = "#2C7BB6") +
  geom_text(aes(label = percent(rental_share, accuracy = 0.1)),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.2))) +
  coord_flip() +
  labs(title = "Long-Term Rental Share by District -- 2010",
       x = NULL, y = "Share of Total Households", caption = caption_2010)
```

---

# Homeownership

```{r}
#| label: homeownership-calc

Homeownership_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    owner_households   = sum(owner_occupied * household_weight, na.rm = TRUE),
    total_households   = sum(household_weight, na.rm = TRUE),
    homeownership_rate = owner_households / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(homeownership_rate))
```

```{r}
#| label: out-homeownership

Homeownership_2010 |>
  mutate(
    owner_households   = comma(round(owner_households)),
    total_households   = comma(round(total_households)),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1)
  ) |>
  kbl(col.names = c("District", "Owner HH", "Total HH", "Ownership Rate"),
      caption   = "Homeownership by District -- 2010 (Weighted)") |>
  kable_styling(latex_options = c("striped", "hold_position"))
```

---

# Household Crowding

```{r}
#| label: crowding-calc

Crowding_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    avg_persons_per_room    = weighted.mean(persons_per_room,    household_weight, na.rm = TRUE),
    avg_persons_per_bedroom = weighted.mean(persons_per_bedroom, household_weight, na.rm = TRUE),
    overcrowding_rate       = weighted.mean(overcrowded,         household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(overcrowding_rate))
```

```{r}
#| label: out-crowding

Crowding_2010 |>
  mutate(
    avg_persons_per_room    = round(avg_persons_per_room, 2),
    avg_persons_per_bedroom = round(avg_persons_per_bedroom, 2),
    overcrowding_rate       = percent(overcrowding_rate, accuracy = 0.1)
  ) |>
  kbl(col.names = c("District", "Persons/Room", "Persons/Bedroom", "Overcrowding Rate"),
      caption   = "Crowding Indicators by District -- 2010 (Weighted)") |>
  kable_styling(latex_options = c("striped", "hold_position"))
```

---

# Housing Quality

```{r}
#| label: quality-calc

Housing_quality_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    piped_water_rate     = weighted.mean(piped_water,     household_weight, na.rm = TRUE),
    electricity_rate     = weighted.mean(electricity,     household_weight, na.rm = TRUE),
    improved_toilet_rate = weighted.mean(improved_toilet, household_weight, na.rm = TRUE),
    durable_walls_rate   = weighted.mean(durable_walls,   household_weight, na.rm = TRUE),
    durable_roof_rate    = weighted.mean(durable_roof,    household_weight, na.rm = TRUE),
    avg_vehicles         = weighted.mean(vehicles_owned,  household_weight, na.rm = TRUE),
    .groups = "drop"
  )
```

```{r}
#| label: out-housing-quality

Housing_quality_2010 |>
  mutate(
    across(piped_water_rate:durable_roof_rate,
           ~ if_else(is.na(.), "NA", percent(., accuracy = 0.1))),
    avg_vehicles = round(avg_vehicles, 2)
  ) |>
  kbl(col.names = c("District", "Piped Water", "Electricity",
                    "Improved Toilet", "Durable Walls", "Durable Roof", "Avg. Vehicles"),
      caption   = "Housing Quality Indicators by District -- 2010 (Weighted)") |>
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

---

# Spare Bedroom Capacity

```{r}
#| label: spare-calc

Spare_bedrooms_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    avg_spare_bedrooms = weighted.mean(spare_bedrooms, household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(avg_spare_bedrooms))
```

```{r}
#| label: out-spare

Spare_bedrooms_2010 |>
  mutate(avg_spare_bedrooms = round(avg_spare_bedrooms, 2)) |>
  kbl(col.names = c("District", "Avg. Spare Bedrooms"),
      caption   = "Average Spare Bedroom Capacity by District -- 2010 (Weighted)") |>
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, position = "center")
```

---

# Hosting Suitability Index

The Hosting Suitability Index (HSI) is the pre-treatment instrument in the
difference-in-differences strategy. A household is classified as hosting-suitable
if it simultaneously has at least one spare bedroom, piped water, public
electricity, and an improved toilet facility. Constructing this index from the
2010 census -- before short-term rental platforms became widely used in
Saint Lucia -- captures pre-existing district characteristics that are
plausibly exogenous to any subsequent platform adoption decisions.

```{r}
#| label: suitability-calc

Suitability_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    suitability_index     = weighted.mean(hosting_suitable, household_weight, na.rm = TRUE),
    suitable_hh_estimated = sum(hosting_suitable * household_weight, na.rm = TRUE),
    total_households      = sum(household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(suitability_index))
```

```{r}
#| label: out-suitability

Suitability_2010 |>
  mutate(
    suitability_index     = percent(suitability_index, accuracy = 0.1),
    suitable_hh_estimated = comma(round(suitable_hh_estimated)),
    total_households      = comma(round(total_households))
  ) |>
  kbl(col.names = c("District", "Suitability Index", "Suitable HH (Est.)", "Total HH"),
      caption   = "Hosting Suitability Index by District -- 2010") |>
  kable_styling(latex_options = c("striped", "hold_position"))
```

```{r}
#| label: fig-suitability

Suitability_2010 |>
  filter(!is.na(suitability_index)) |>
  ggplot(aes(x = reorder(district, suitability_index),
             y = suitability_index,
             fill = suitability_index)) +
  geom_col() +
  geom_text(aes(label = percent(suitability_index, accuracy = 0.1)),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.2))) +
  scale_fill_gradient(low = "#fee8c8", high = "#e34a33", guide = "none") +
  coord_flip() +
  labs(
    title    = "Hosting Suitability Index by District -- 2010",
    subtitle = "Share of households with spare bedroom, piped water, electricity and improved toilet",
    x = NULL, y = "Suitability Index (%)",
    caption = caption_2010
  )
```

---

# District Summary

```{r}
#| label: out-summary

District_Summary_2010 <- Rental_supply_2010 |>
  select(district, total_households, rental_share) |>
  left_join(Homeownership_2010  |> select(district, homeownership_rate), by = "district") |>
  left_join(Crowding_2010       |> select(district, overcrowding_rate),  by = "district") |>
  left_join(Suitability_2010    |> select(district, suitability_index),  by = "district") |>
  left_join(Housing_quality_2010|> select(district, piped_water_rate, electricity_rate),
            by = "district") |>
  mutate(census_year = 2010L)

District_Summary_2010 |>
  mutate(
    total_households   = comma(round(total_households)),
    rental_share       = percent(rental_share,       accuracy = 0.1),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1),
    overcrowding_rate  = percent(overcrowding_rate,  accuracy = 0.1),
    suitability_index  = if_else(is.na(suitability_index), "NA",
                                 percent(suitability_index, accuracy = 0.1)),
    piped_water_rate   = if_else(is.na(piped_water_rate), "NA",
                                 percent(piped_water_rate, accuracy = 0.1)),
    electricity_rate   = percent(electricity_rate,   accuracy = 0.1)
  ) |>
  select(district, total_households, rental_share, homeownership_rate,
         overcrowding_rate, suitability_index, piped_water_rate, electricity_rate) |>
  kbl(
    col.names = c("District", "Total HH", "Rental Share", "Ownership Rate",
                  "Overcrowding", "Suitability", "Piped Water", "Electricity"),
    caption   = "District Housing Indicators -- 2010"
  ) |>
  kable_styling(latex_options = c("striped", "hold_position", "scale_down")) |>
  add_header_above(c(" " = 2, "Tenure" = 2, "Crowding" = 1, "STR Exposure" = 3))
```

---

# Pre-Treatment Relationship

The figure below shows the cross-sectional relationship between the 2010
Hosting Suitability Index and the long-term rental share by district.
A positive association is expected -- more suitable districts naturally
attract more renters. This baseline correlation is not a causal finding.
The causal argument in the thesis concerns whether districts with higher
pre-treatment suitability experienced larger changes in housing outcomes
between 2010 and 2022.

```{r}
#| label: fig-suitability-rental

District_Summary_2010 |>
  filter(!is.na(suitability_index), !is.na(rental_share)) |>
  ggplot(aes(x = suitability_index, y = rental_share, label = district)) +
  geom_point(aes(size = total_households), color = "#2C7BB6", alpha = 0.7) +
  geom_text_repel(size = 3.2, max.overlaps = 12) +
  geom_smooth(method = "lm", se = TRUE, color = "#D7191C",
              linewidth = 0.8, linetype = "dashed") +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  scale_size_continuous(labels = comma, range = c(2, 8),
                        guide  = guide_legend(title = "Total HH")) +
  labs(
    title   = "2010 Hosting Suitability vs Rental Share",
    subtitle = "Pre-treatment baseline relationship by district",
    x       = "Hosting Suitability Index (2010)",
    y       = "Long-Term Rental Share (2010)",
    caption = caption_2010
  )
```
