---
title: "2010 Census Data — Exploration & Diagnosis"
subtitle: "Saint Lucia Housing Thesis | Pre-Treatment Baseline"
author: "Mave Kimara Alexander"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Contents"
    number-sections: true
    theme: flatly
    code-fold: true
    code-tools: true
    df-print: kable
    fig-width: 8
    fig-height: 5
    embed-resources: true
execute:
  warning: false
  message: false
  echo: true
---

```{r setup}
#| label: setup
#| include: false

library(haven)
library(tidyverse)
library(labelled)
library(kableExtra)
library(scales)
library(ggrepel)

theme_set(
  theme_minimal(base_size = 11) +
  theme(
    plot.title    = element_text(face = "bold", size = 12),
    plot.subtitle = element_text(size = 10, color = "grey40"),
    plot.caption  = element_text(size = 8,  color = "grey55"),
    axis.text     = element_text(size = 9),
    legend.position = "bottom",
    legend.text   = element_text(size = 9)
  )
)

caption_2010 <- "Source: Saint Lucia Population and Housing Census 2010"
```

---

::: {.callout-note}
## Why does the 2010 census matter?

The 2010 census is the **pre-treatment baseline** for your entire thesis.
Without it, you only have a cross-sectional snapshot of 2022 — 
you cannot prove that *anything caused anything*.

With the 2010 data you can:

1. **Compute change** — ∆rental share, ∆homeownership, ∆overcrowding per district (2010→2022)
2. **Build the pre-treatment Hosting Suitability Index** — the key instrument in your identification strategy (districts suited for Airbnb *before* Airbnb existed)
3. **Check parallel trends** — verify that high- and low-suitability districts were not already diverging before the 2014 shock
4. **Run the DiD** — regress outcome changes on pre-treatment suitability interacted with the post-treatment indicator

The NA problems in the current code break step 2. This document diagnoses and fixes them.
:::

---

# Loading the 2010 Data

```{r load}
Raw_Census_Data_2010 <- read_sav("person_house_merged.sav")

cat("Rows:", nrow(Raw_Census_Data_2010), "\n")
cat("Columns:", ncol(Raw_Census_Data_2010), "\n")
```

---

# Diagnosing the NA Problem

The 2010 Housing Quality table shows `NA` for piped water, improved toilet, durable walls,
and durable roof across **every district**. Electricity is fine. The NA-cleaning step converts
value `9` to `NA` — but value `9` may be a **legitimate category** for some variables.
Let's check the raw distributions.

## Water Source (H18_WATER)

```{r diag-water}
Raw_Census_Data_2010 |>
  filter(!is.na(H18_WATER)) |>
  count(H18_WATER) |>
  mutate(
    label    = as.character(labelled::val_label(Raw_Census_Data_2010$H18_WATER[1])),
    value    = as.numeric(H18_WATER),
    pct      = n / sum(n)
  ) |>
  mutate(value_labels = sapply(value, function(v) {
    lbls <- labelled::val_labels(Raw_Census_Data_2010$H18_WATER)
    nm   <- names(lbls)[lbls == v]
    if (length(nm) == 0) paste0("Code ", v, " (no label)") else nm
  })) |>
  select(H18_WATER, value_labels, n, pct) |>
  mutate(pct = percent(pct, accuracy = 0.1)) |>
  kbl(col.names = c("Code", "Label", "Count", "Share"),
      caption = "Raw distribution of H18_WATER (water source) — 2010") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

::: {.callout-warning}
If value `9` = "Not Stated" and is common, the NA-cleaning line
`if_else(. %in% c(..., 9), NA_real_, ...)` converts a real (non-missing)
category to NA — breaking any indicator computed from it.
The fix is to **not** treat `9` as missing for these variables, or to
recode it as `0` in the quality indicator (i.e. "does not have piped water").
:::

## Toilet Type (H20_TOILET)

```{r diag-toilet}
Raw_Census_Data_2010 |>
  filter(!is.na(H20_TOILET)) |>
  count(H20_TOILET) |>
  mutate(value_labels = sapply(as.numeric(H20_TOILET), function(v) {
    lbls <- labelled::val_labels(Raw_Census_Data_2010$H20_TOILET)
    nm   <- names(lbls)[lbls == v]
    if (length(nm) == 0) paste0("Code ", v, " (no label)") else nm
  })) |>
  mutate(pct = percent(n / sum(n), accuracy = 0.1)) |>
  select(H20_TOILET, value_labels, n, pct) |>
  kbl(col.names = c("Code", "Label", "Count", "Share"),
      caption = "Raw distribution of H20_TOILET — 2010") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Wall Material (H15_WALLS)

```{r diag-walls}
Raw_Census_Data_2010 |>
  filter(!is.na(H15_WALLS)) |>
  count(H15_WALLS) |>
  mutate(value_labels = sapply(as.numeric(H15_WALLS), function(v) {
    lbls <- labelled::val_labels(Raw_Census_Data_2010$H15_WALLS)
    nm   <- names(lbls)[lbls == v]
    if (length(nm) == 0) paste0("Code ", v, " (no label)") else nm
  })) |>
  mutate(pct = percent(n / sum(n), accuracy = 0.1)) |>
  select(H15_WALLS, value_labels, n, pct) |>
  kbl(col.names = c("Code", "Label", "Count", "Share"),
      caption = "Raw distribution of H15_WALLS — 2010") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Roof Material (H16_ROOF)

```{r diag-roof}
Raw_Census_Data_2010 |>
  filter(!is.na(H16_ROOF)) |>
  count(H16_ROOF) |>
  mutate(value_labels = sapply(as.numeric(H16_ROOF), function(v) {
    lbls <- labelled::val_labels(Raw_Census_Data_2010$H16_ROOF)
    nm   <- names(lbls)[lbls == v]
    if (length(nm) == 0) paste0("Code ", v, " (no label)") else nm
  })) |>
  mutate(pct = percent(n / sum(n), accuracy = 0.1)) |>
  select(H16_ROOF, value_labels, n, pct) |>
  kbl(col.names = c("Code", "Label", "Count", "Share"),
      caption = "Raw distribution of H16_ROOF — 2010") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Lighting Source (H21_LIGHTING) — should be fine

```{r diag-lighting}
Raw_Census_Data_2010 |>
  filter(!is.na(H21_LIGHTING)) |>
  count(H21_LIGHTING) |>
  mutate(value_labels = sapply(as.numeric(H21_LIGHTING), function(v) {
    lbls <- labelled::val_labels(Raw_Census_Data_2010$H21_LIGHTING)
    nm   <- names(lbls)[lbls == v]
    if (length(nm) == 0) paste0("Code ", v, " (no label)") else nm
  })) |>
  mutate(pct = percent(n / sum(n), accuracy = 0.1)) |>
  select(H21_LIGHTING, value_labels, n, pct) |>
  kbl(col.names = c("Code", "Label", "Count", "Share"),
      caption = "Raw distribution of H21_LIGHTING — 2010") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

---

# Fixed Working Table

::: {.callout-tip}
## Fix applied
The corrected NA cleaning only sets **true system missing** codes
(`-999999999`, `999999999`) to `NA`. Values like `9` ("Not Stated") or
`99` ("Not Stated") are treated as legitimate responses — specifically, a
`9` in water source means "does not have piped water" and should result
in `piped_water = 0`, not a dropped row.
:::

```{r working-table}
Raw_Census_Data_2010 <- Raw_Census_Data_2010 |>
  mutate(household_id_2010 = paste(DISTRICT, ED, HH, sep = "_"))

Thesis_Working_Data_2010 <- Raw_Census_Data_2010 |>
  distinct(household_id_2010, .keep_all = TRUE) |>
  select(
    household_id_2010,
    DISTRICT, poldist,
    NPERS,
    H11_TYPE, H13_OWN,
    H15_WALLS, H16_ROOF, H17_YR_BUILT,
    H18_WATER, H20_TOILET, H21_LIGHTING,
    H23_ROOMS, H24_BEDROOMS,
    H30_VEHICLES,
    HWEIGHT
  ) |>
  rename(
    household_id    = household_id_2010,
    district_raw    = DISTRICT,
    constituency    = poldist,
    household_size  = NPERS,
    building_type   = H11_TYPE,
    tenure_status   = H13_OWN,
    wall_material   = H15_WALLS,
    roof_material   = H16_ROOF,
    year_built      = H17_YR_BUILT,
    water_source    = H18_WATER,
    toilet_type     = H20_TOILET,
    lighting_source = H21_LIGHTING,
    rooms           = H23_ROOMS,
    bedrooms        = H24_BEDROOMS,
    vehicles_owned  = H30_VEHICLES,
    household_weight = HWEIGHT
  ) |>
  zap_labels() |>
  mutate(
    # District mapping
    district = case_when(
      district_raw == 1  ~ "Castries 1",
      district_raw == 2  ~ "Castries 2",
      district_raw == 3  ~ "Castries 3",
      district_raw == 4  ~ "Anse La Raye",
      district_raw == 5  ~ "Canaries",
      district_raw == 6  ~ "Soufriere",
      district_raw == 7  ~ "Choiseul",
      district_raw == 8  ~ "Laborie",
      district_raw == 9  ~ "Vieux Fort",
      district_raw == 10 ~ "Micoud",
      district_raw == 11 ~ "Dennery",
      district_raw == 12 ~ "Gros Islet",
      TRUE               ~ paste0("Unknown (", district_raw, ")")
    ),
    
    # Tenure
    owner_occupied    = if_else(tenure_status %in% c(1, 2), 1L, 0L),
    long_term_rental  = if_else(tenure_status %in% c(3, 4), 1L, 0L),
    
    # ---------------------------------------------------------------
    # FIXED: only treat true system-missing as NA
    # Do NOT include 9 or 99 here — they are "Not Stated" categories
    # that simply mean the household lacks that amenity.
    # ---------------------------------------------------------------
    across(
      c(household_size, building_type, tenure_status, wall_material,
        roof_material, year_built, water_source, toilet_type,
        lighting_source, rooms, bedrooms, vehicles_owned),
      ~ if_else(. %in% c(-999999999, 999999999), NA_real_, as.numeric(.))
    ),
    
    # Housing quality indicators
    # Check the raw distributions above to confirm which codes = "Not Stated"
    # and adjust these if needed after running the diagnostics.
    piped_water    = if_else(water_source    %in% c(1, 2), 1L, 0L,   missing = NA_integer_),
    electricity    = if_else(lighting_source == 1,         1L, 0L,   missing = NA_integer_),
    improved_toilet= if_else(toilet_type     %in% c(1, 2, 3), 1L, 0L, missing = NA_integer_),
    durable_walls  = if_else(wall_material   %in% c(1, 2, 3), 1L, 0L, missing = NA_integer_),
    durable_roof   = if_else(roof_material   %in% c(1, 2, 3), 1L, 0L, missing = NA_integer_),
    
    # Crowding
    rooms_clean          = if_else(rooms    > 0, rooms,    NA_real_),
    bedrooms_clean       = if_else(bedrooms > 0, bedrooms, NA_real_),
    persons_per_room     = household_size / rooms_clean,
    persons_per_bedroom  = household_size / bedrooms_clean,
    overcrowded          = if_else(persons_per_bedroom > 2, 1L, 0L),
    
    # Spare capacity
    spare_bedrooms = bedrooms_clean - household_size,
    
    # Hosting suitability
    hosting_suitable = if_else(
      spare_bedrooms  > 0 &
      piped_water     == 1 &
      electricity     == 1 &
      improved_toilet == 1,
      1L, 0L
    ),
    
    census_year = 2010L
  ) |>
  filter(!is.na(district))

cat("Households:", nrow(Thesis_Working_Data_2010), "\n")
cat("Districts:", n_distinct(Thesis_Working_Data_2010$district), "\n")

Thesis_Working_Data_2010 |>
  count(district, name = "households") |>
  arrange(district) |>
  kbl(caption = "Household count per district after fix") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

---

# Post-Fix Quality Check

Before producing any summaries, verify that the NAs are now resolved.

```{r quality-check}
Thesis_Working_Data_2010 |>
  summarise(
    across(
      c(piped_water, electricity, improved_toilet, durable_walls, durable_roof,
        rooms_clean, bedrooms_clean, overcrowded, spare_bedrooms, hosting_suitable),
      ~ mean(is.na(.)),
      .names = "pct_na_{.col}"
    )
  ) |>
  pivot_longer(everything(), names_to = "variable", values_to = "pct_missing") |>
  mutate(
    variable    = str_remove(variable, "pct_na_"),
    pct_missing = percent(pct_missing, accuracy = 0.1),
    status      = if_else(pct_missing == "0.0%", "✅ No NAs", "⚠️ Has NAs")
  ) |>
  kbl(col.names = c("Variable", "% Missing", "Status"),
      caption   = "NA check for key derived variables") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

::: {.callout-important}
If any variable still shows high missingness after the fix, run the
raw distribution chunks in Section 2 and look at which codes are
common. You may need to adjust the `%in%` vectors for the quality
indicators above to match the 2010 codebook exactly.
:::

---

# District-Level Summaries

## Rental Supply (2010)

```{r rental-supply}
Rental_supply_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    long_term_rentals = sum(long_term_rental * household_weight, na.rm = TRUE),
    total_households  = sum(household_weight, na.rm = TRUE),
    rental_share      = long_term_rentals / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(rental_share))

Rental_supply_2010 |>
  mutate(
    long_term_rentals = comma(round(long_term_rentals)),
    total_households  = comma(round(total_households)),
    rental_share      = percent(rental_share, accuracy = 0.1)
  ) |>
  kbl(col.names = c("District", "Long-Term Rentals", "Total HH", "Rental Share"),
      caption   = "Long-Term Rental Supply by District — 2010 (Weighted)") |>
  kable_styling(bootstrap_options = c("striped", "hover"))
```

```{r rental-supply-plot}
Rental_supply_2010 |>
  ggplot(aes(x = reorder(district, rental_share), y = rental_share)) +
  geom_col(fill = "#2C7BB6") +
  geom_text(aes(label = percent(rental_share, accuracy = 0.1)),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = percent,
                     expand = expansion(mult = c(0, 0.2))) +
  coord_flip() +
  labs(title   = "Long-Term Rental Share by District — 2010",
       x = NULL, y = "Share of Total Households",
       caption = caption_2010)
```

## Homeownership (2010)

```{r homeownership}
Homeownership_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    owner_households  = sum(owner_occupied * household_weight, na.rm = TRUE),
    total_households  = sum(household_weight, na.rm = TRUE),
    homeownership_rate = owner_households / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(homeownership_rate))

Homeownership_2010 |>
  mutate(
    owner_households   = comma(round(owner_households)),
    total_households   = comma(round(total_households)),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1)
  ) |>
  kbl(col.names = c("District", "Owner HH", "Total HH", "Ownership Rate"),
      caption   = "Homeownership by District — 2010 (Weighted)") |>
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Crowding (2010)

```{r crowding}
Crowding_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    avg_persons_per_room    = weighted.mean(persons_per_room,    household_weight, na.rm = TRUE),
    avg_persons_per_bedroom = weighted.mean(persons_per_bedroom, household_weight, na.rm = TRUE),
    overcrowding_rate       = weighted.mean(overcrowded,         household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(overcrowding_rate))

Crowding_2010 |>
  mutate(
    avg_persons_per_room    = round(avg_persons_per_room, 2),
    avg_persons_per_bedroom = round(avg_persons_per_bedroom, 2),
    overcrowding_rate       = percent(overcrowding_rate, accuracy = 0.1)
  ) |>
  kbl(col.names = c("District", "Persons/Room", "Persons/Bedroom", "Overcrowding Rate"),
      caption   = "Crowding Indicators by District — 2010 (Weighted)") |>
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Housing Quality (2010)

```{r housing-quality}
Housing_quality_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    piped_water_rate     = weighted.mean(piped_water,     household_weight, na.rm = TRUE),
    electricity_rate     = weighted.mean(electricity,     household_weight, na.rm = TRUE),
    improved_toilet_rate = weighted.mean(improved_toilet, household_weight, na.rm = TRUE),
    durable_walls_rate   = weighted.mean(durable_walls,   household_weight, na.rm = TRUE),
    durable_roof_rate    = weighted.mean(durable_roof,    household_weight, na.rm = TRUE),
    avg_vehicles         = weighted.mean(vehicles_owned,  household_weight, na.rm = TRUE),
    .groups = "drop"
  )

Housing_quality_2010 |>
  mutate(
    across(piped_water_rate:durable_roof_rate, ~ percent(., accuracy = 0.1)),
    avg_vehicles = round(avg_vehicles, 2)
  ) |>
  kbl(col.names = c("District", "Piped Water", "Electricity",
                    "Improved Toilet", "Durable Walls", "Durable Roof", "Avg. Vehicles"),
      caption   = "Housing Quality by District — 2010 (Weighted)") |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) |>
  scroll_box(width = "100%")
```

::: {.callout-note}
If any column above still shows `NA`, check the raw distribution for that variable in
Section 2 and update the indicator coding. For example, if `piped_water_rate` is still
`NA`, look at what codes `water_source` actually contains and adjust
`piped_water = if_else(water_source %in% c(1, 2), ...)` to match.
:::

## Spare Bedroom Capacity (2010)

```{r spare-bedrooms}
Spare_bedrooms_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    avg_spare_bedrooms = weighted.mean(spare_bedrooms, household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(avg_spare_bedrooms))

Spare_bedrooms_2010 |>
  mutate(avg_spare_bedrooms = round(avg_spare_bedrooms, 2)) |>
  kbl(col.names = c("District", "Avg. Spare Bedrooms"),
      caption   = "Spare Bedroom Capacity by District — 2010 (Weighted)") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

---

# The Hosting Suitability Index (2010)

::: {.callout-important}
## This is the heart of your identification strategy

The Hosting Suitability Index (HSI) is your **pre-treatment instrument**.
A household is "hosting suitable" if it has:

- At least one **spare bedroom** (capacity for a guest)
- **Piped water** (minimum comfort standard)
- **Electricity** (modern utility)
- **Improved toilet** (sanitation standard)

By computing this from the **2010 census** — before Airbnb became widely
used in Saint Lucia — you capture which districts *were already set up*
for short-term rental hosting, independent of any subsequent platform
adoption decisions.

In your DiD, the district-level HSI from 2010 becomes the "treatment
intensity" variable: districts with a higher 2010 HSI are predicted to
have been more exposed to the Airbnb shock, and you test whether those
districts experienced larger housing market changes between 2010 and 2022.
:::

```{r suitability}
Suitability_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    suitability_index      = weighted.mean(hosting_suitable, household_weight, na.rm = TRUE),
    suitable_hh_estimated  = sum(hosting_suitable * household_weight, na.rm = TRUE),
    total_households       = sum(household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(suitability_index))

Suitability_2010 |>
  mutate(
    suitability_index     = percent(suitability_index, accuracy = 0.1),
    suitable_hh_estimated = comma(round(suitable_hh_estimated)),
    total_households      = comma(round(total_households))
  ) |>
  kbl(col.names = c("District", "Suitability Index", "Suitable HH (Est.)", "Total HH"),
      caption   = "Hosting Suitability Index by District — 2010") |>
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

```{r suitability-plot}
Suitability_2010 |>
  filter(!is.na(suitability_index)) |>
  ggplot(aes(x = reorder(district, suitability_index),
             y = suitability_index,
             fill = suitability_index)) +
  geom_col() +
  geom_text(aes(label = percent(suitability_index, accuracy = 0.1)),
            hjust = -0.1, size = 3) +
  scale_y_continuous(labels = percent,
                     expand = expansion(mult = c(0, 0.2))) +
  scale_fill_gradient(low = "#fee8c8", high = "#e34a33", guide = "none") +
  coord_flip() +
  labs(
    title    = "Hosting Suitability Index by District — 2010",
    subtitle = "Share of households with spare bedroom, piped water, electricity & improved toilet",
    x = NULL, y = "Suitability Index (%)",
    caption = caption_2010
  )
```

---

# District Summary Table (2010)

```{r summary-table}
District_Summary_2010 <- Rental_supply_2010 |>
  select(district, total_households, rental_share) |>
  left_join(Homeownership_2010 |> select(district, homeownership_rate), by = "district") |>
  left_join(Crowding_2010      |> select(district, overcrowding_rate),  by = "district") |>
  left_join(Suitability_2010   |> select(district, suitability_index),  by = "district") |>
  left_join(Housing_quality_2010 |> select(district, piped_water_rate, electricity_rate),
            by = "district") |>
  mutate(census_year = 2010L)

District_Summary_2010 |>
  mutate(
    total_households   = comma(round(total_households)),
    rental_share       = percent(rental_share,       accuracy = 0.1),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1),
    overcrowding_rate  = percent(overcrowding_rate,  accuracy = 0.1),
    suitability_index  = percent(suitability_index,  accuracy = 0.1),
    piped_water_rate   = percent(piped_water_rate,   accuracy = 0.1),
    electricity_rate   = percent(electricity_rate,   accuracy = 0.1)
  ) |>
  select(district, total_households, rental_share, homeownership_rate,
         overcrowding_rate, suitability_index, piped_water_rate, electricity_rate) |>
  kbl(
    col.names = c("District", "Total HH", "Rental Share",
                  "Ownership Rate", "Overcrowding",
                  "Suitability", "Piped Water", "Electricity"),
    caption = "District Housing Indicators — 2010 (complete)"
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) |>
  add_header_above(c(" " = 2, "Tenure" = 2, "Wellbeing" = 1, "STR Potential" = 3)) |>
  scroll_box(width = "100%")
```

---

# Thesis Interpretation

## What does the 2010 baseline tell us?

```{r interpretation-plot}
#| fig-height: 6

# Rental share vs suitability index — the key relationship for your thesis
District_Summary_2010 |>
  filter(!is.na(suitability_index), !is.na(rental_share)) |>
  ggplot(aes(x = suitability_index, y = rental_share, label = district)) +
  geom_point(aes(size = total_households),
             color = "#2C7BB6", alpha = 0.7) +
  geom_text_repel(size = 3.2, max.overlaps = 12) +
  geom_smooth(method = "lm", se = TRUE, color = "#D7191C",
              linewidth = 0.8, linetype = "dashed") +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  scale_size_continuous(labels = comma, range = c(2, 8),
                        guide  = guide_legend(title = "Total HH")) +
  labs(
    title    = "2010 Hosting Suitability vs Rental Share",
    subtitle = "Pre-treatment relationship: more suitable districts had higher initial rental share",
    x        = "Hosting Suitability Index (2010)",
    y        = "Long-Term Rental Share (2010)",
    caption  = caption_2010
  )
```

::: {.callout-tip}
## Interpreting this chart for your thesis

A **positive slope** here is expected — districts with more suitable
housing stock naturally also have more renters. This is **not** a causal
finding; it's a baseline correlation.

The causal story in your thesis is the *change* version of this: after 2014,
did districts with higher 2010 suitability experience **larger increases in
rental share** or **larger decreases in homeownership**? That's the DiD estimate.
:::

---

# What to Do Next

After confirming the NA fix works, your next steps are:

1. **Run this Quarto document** to confirm all quality indicators now have real values.
   Look at the raw distribution tables in Section 2 — if any variable still has
   unexpected NAs, adjust the coding in Section 3.

2. **Save `District_Summary_2010`** — this feeds directly into your DiD panel when
   combined with `District_Summary_2022`.

3. **Cross-check the district mapping** with Diana at the Statistics Office —
   particularly whether Districts 1/2/3 in 2010 map cleanly to Districts 1/2/3 in 2022.

4. **Build the DiD panel** by stacking 2010 and 2022 district summaries, then
   computing the change in each outcome variable. The 2010 suitability index
   becomes your treatment intensity measure.
