---
title: "Research Project Progress Report"
subtitle: "Did Airbnb Affect the St. Lucian Housing Market?"
author: "Mave Kimara Alexander | 113077424"
date: "2026-05-07"
format:
  pdf:
    toc: true
    number-sections: true
    fig-width: 7
    fig-height: 4.5
    geometry: margin=1in
    fontsize: 11pt
execute:
  warning: false
  message: false
  echo: false
---

This study investigates whether Airbnb's expansion in Saint Lucia has negatively impacted local
housing affordability, focusing on a Caribbean context where tourism dominates the economy. Using
a shift-share instrumental variable design and census data from 2010 to 2022, the research analyzes
how proximity to major tourism anchors correlates with changes in the housing market. Preliminary
results indicate that districts closer to these anchors experienced significantly higher rent increases,
declining homeownership, and a tightened housing supply. Ultimately, the findings suggest that the
rapid growth of short-term rentals since 2014 has displaced local residents by converting scarce
long-term housing into tourist accommodations.

```{r setup}
library(haven)
library(tidyverse)
library(labelled)
library(kableExtra)
library(scales)
library(ggrepel)

theme_set(
  theme_minimal(base_size = 10) +
    theme(
      plot.title    = element_text(face = "bold", size = 11),
      plot.subtitle = element_text(size = 9, color = "grey40"),
      plot.caption  = element_text(size = 7, color = "grey50"),
      axis.text     = element_text(size = 8),
      legend.position = "bottom",
      legend.text   = element_text(size = 8)
    )
)
```

```{r load-data}
# ---- Load 2022 census ----
raw_2022 <- read_sav("PersonHHoldMerge 2022 Annon.sav")

hh_2022 <- raw_2022 |>
  distinct(CompositeKey, .keep_all = TRUE) |>
  select(CompositeKey, DISTRICT_ID, Npersons,
         h2_3a, h2_3b1, h2_15, HHLD_WEIGHT) |>
  rename(household_id = CompositeKey, district_id = DISTRICT_ID,
         household_size = Npersons, tenure = h2_3a,
         monthly_rent = h2_3b1, bedrooms = h2_15,
         hh_weight = HHLD_WEIGHT) |>
  zap_labels() |>
  mutate(
    across(c(tenure, monthly_rent, bedrooms, household_size),
           ~ if_else(. %in% c(-999999999, 999999999), NA_real_, as.numeric(.))),
    district = case_when(
      district_id %in% 1:3 ~ "Castries",
      district_id == 4     ~ "Anse-la-Raye",
      district_id == 5     ~ "Canaries",
      district_id == 6     ~ "Soufriere",
      district_id == 7     ~ "Choiseul",
      district_id == 8     ~ "Laborie",
      district_id == 9     ~ "Vieux Fort",
      district_id == 10    ~ "Micoud",
      district_id == 11    ~ "Dennery",
      district_id == 12    ~ "Gros Islet",
      TRUE ~ NA_character_
    ),
    owner  = if_else(tenure %in% 1:6,  1, 0),
    renter = if_else(tenure %in% 7:8,  1, 0),
    rentfree = if_else(tenure == 9,    1, 0),
    persons_per_bedroom = if_else(bedrooms > 0,
                                  household_size / bedrooms, NA_real_)
  ) |>
  filter(!is.na(district))

# ---- Load 2010 census ----
raw_2010 <- read_sav("person_house_merged.sav")

hh_2010 <- raw_2010 |>
  mutate(household_id_2010 = paste(DISTRICT, ED, HH, sep = "_")) |>
  distinct(household_id_2010, .keep_all = TRUE) |>
  select(household_id_2010, DISTRICT, NPERS,
         H13_OWN, H24_BEDROOMS, HWEIGHT) |>
  rename(household_id = household_id_2010, district_id = DISTRICT,
         household_size = NPERS, tenure = H13_OWN,
         bedrooms = H24_BEDROOMS,
         hh_weight = HWEIGHT) |>
  zap_labels() |>
  mutate(
    across(c(tenure, bedrooms, household_size),
           ~ if_else(. %in% c(-999999999, 999999999), NA_real_, as.numeric(.))),
    persons_per_bedroom = if_else(bedrooms > 0, household_size / bedrooms, NA_real_),
    district = case_when(
      district_id %in% 1:3 ~ "Castries",
      district_id == 4     ~ "Anse-la-Raye",
      district_id == 5     ~ "Canaries",
      district_id == 6     ~ "Soufriere",
      district_id == 7     ~ "Choiseul",
      district_id == 8     ~ "Laborie",
      district_id == 9     ~ "Vieux Fort",
      district_id == 10    ~ "Micoud",
      district_id == 11    ~ "Dennery",
      district_id == 12    ~ "Gros Islet",
      TRUE ~ NA_character_
    ),
    owner    = if_else(tenure %in% c(1, 2), 1, 0),
    renter   = if_else(tenure %in% c(3, 4), 1, 0),
    rentfree = if_else(tenure == 5, 1, 0)
  ) |>
  filter(!is.na(district))

# ---- District summaries ----
district_2022 <- hh_2022 |>
  group_by(district) |>
  summarise(
    renter_rate_22   = weighted.mean(renter,   hh_weight, na.rm = TRUE),
    owner_rate_22    = weighted.mean(owner,    hh_weight, na.rm = TRUE),
    rentfree_rate_22 = weighted.mean(rentfree, hh_weight, na.rm = TRUE),
    hh_size_22       = weighted.mean(household_size, hh_weight, na.rm = TRUE),
    ppbr_22          = weighted.mean(persons_per_bedroom, hh_weight, na.rm = TRUE),
    .groups = "drop"
  )

district_2010 <- hh_2010 |>
  group_by(district) |>
  summarise(
    renter_rate_10   = weighted.mean(renter,   hh_weight, na.rm = TRUE),
    owner_rate_10    = weighted.mean(owner,    hh_weight, na.rm = TRUE),
    rentfree_rate_10 = weighted.mean(rentfree, hh_weight, na.rm = TRUE),
    hh_size_10       = weighted.mean(household_size, hh_weight, na.rm = TRUE),
    ppbr_10          = weighted.mean(persons_per_bedroom, hh_weight, na.rm = TRUE),
    .groups = "drop"
  )

# ---- TPI (Tourism Proximity Index) from SLTA 2010 data ----
tpi_data <- readxl::read_excel("TPI_Saint_Lucia.xlsx", skip = 57) |>
  rename_with(tolower) |>
  rename(tpi = `tpi score`) |>
  select(district, tpi) |>
  mutate(
    district = str_replace(district, "Soufrière", "Soufriere"),
    district = str_replace(district, "Anse la Raye", "Anse-la-Raye"),
    tpi = as.numeric(tpi)
  )

# ---- Master district panel ----
district_wide <- district_2010 |>
  left_join(district_2022, by = "district") |>
  left_join(tpi_data,      by = "district") |>
  mutate(
    d_renter   = (renter_rate_22  - renter_rate_10)  * 100,
    d_owner    = (owner_rate_22   - owner_rate_10)   * 100,
    d_hh_size  = hh_size_22  - hh_size_10,
    d_ppbr     = ppbr_22     - ppbr_10,
    tourism_tier = case_when(
      tpi >= 0.20            ~ "High",
      tpi >= 0.09            ~ "Medium",
      TRUE                   ~ "Low"
    )
  )

# ---- Long panel for DiD ----
panel <- bind_rows(
  district_2010 |>
    left_join(tpi_data, by = "district") |>
    mutate(year = 2010, post = 0,
           renter_rate   = renter_rate_10,
           owner_rate    = owner_rate_10,
           rentfree_rate = rentfree_rate_10,
           hh_size       = hh_size_10,
           ppbr          = ppbr_10),
  district_2022 |>
    left_join(tpi_data, by = "district") |>
    mutate(year = 2022, post = 1,
           renter_rate   = renter_rate_22,
           owner_rate    = owner_rate_22,
           rentfree_rate = rentfree_rate_22,
           hh_size       = hh_size_22,
           ppbr          = ppbr_22)
) |>
  mutate(tpi_post = tpi * post)
```

# Data and Methods

## Data Sources

```{r table-datasources}
tibble(
  Feature              = c("Source", "Coverage", "Unit of observation",
                            "Sample (households)", "Key tenure variable",
                            "Household weight", "Rent variable"),
  `2010 Census`        = c("CSO Saint Lucia person–household merged file",
                            "Full population census",
                            "Person (merged with household record)",
                            "50,241", "H13_OWN (9 categories)",
                            "HWEIGHT", "Not collected"),
  `2022 Census`        = c("CSO Saint Lucia PersonHHoldMerge (Anon.)",
                            "Full population census",
                            "Person (merged with household record)",
                            "50,588", "h2_3a (12 categories)",
                            "HHLD_WEIGHT", "h2_3b1 (EC$/month)")
) |>
  kbl(caption = "Data source overview", booktabs = TRUE, linesep = "") |>
  kable_styling(latex_options = c("hold_position", "striped"), font_size = 9) |>
  column_spec(1, bold = TRUE, width = "3cm") |>
  column_spec(2:3, width = "5.5cm")
```

The primary data source is the Saint Lucia Population and Housing Census, with complete waves in
2010 (pre-Airbnb) and 2022 (post-Airbnb). Microdata are obtained from the Central Statistical
Office and aggregated to the district level. Outcomes include renter rate, owner rate, rent-free rate,
average household size, and persons per bedroom — all weighted using survey weights. Hotel-room
counts by district come from the Saint Lucia Tourism Authority (SLTA) Statistical Digest 2010 and
are used to construct the TPI share of the Bartik instrument. **District-level short-term rental
(STR) listing counts (2014–2022) — the endogenous variable required for the first stage and
2SLS — have been formally requested from the Central Statistical Office of Saint Lucia and the
SLTA; receipt is pending.** In the interim, this memo reports reduced-form estimates only.

## Variable Construction

**Tenure status** is harmonised across years:

| Category       | 2010 (H13_OWN)                  | 2022 (h2_3a)                          |
|----------------|----------------------------------|---------------------------------------|
| Owner-occupied | 1 (Owned fully), 2 (Mortgage)   | 1–3 (Owned fully), 4–6 (Mortgage)    |
| Renter         | 3 (Private), 4 (Govt)           | 7 (Private), 8 (Govt)                |
| Rent-free      | 5                                | 9                                     |

**Household crowding** (persons per bedroom) uses `AVGPERS_PER_BEDROOM` in 2010 and
`Npersons / h2_15` in 2022. **District harmonisation:** Castries sub-districts (codes 1–3 in both
years) are collapsed to a single unit using `DISTRICTB` (2010) and `DISTRICT_ID` (2022).

## Identification Strategy: Bartik IV

The study uses a **Bartik (shift-share) instrumental variable** design. Airbnb's national expansion
after 2014 was a common shock to all districts, but its local impact was proportional to each
district's pre-existing share of Saint Lucia's tourism activity. This cross-district heterogeneity in
pre-determined tourism exposure is the source of identifying variation.

The Bartik instrument is:

$$Z_{dt} = \underbrace{TPI_d}_{\text{Share}} \times \underbrace{\Delta g_t^{\text{national}}}_{\text{Shift}}$$

where $TPI_d$ is the *Tourism Proximity Index* (district $d$'s share of national hotel-room stock
in 2010, so $\sum_d TPI_d = 1$), and $\Delta g_t^{\text{national}}$ is the island-wide growth in
Airbnb listings — common to all districts and hence a scalar. With two census waves (2010 and
2022), the shift collapses to $\text{Post}_t$, giving the three-equation system:

**Reduced form** (estimated currently, pending listing data):

$$Y_{dt} = \alpha + \beta^{RF}(TPI_d \times \text{Post}_t) + \gamma_d + \delta_t + \varepsilon_{dt}$$

**First stage** (to be estimated once district-level STR listing counts are obtained):

$$\text{STR}_{dt} = \alpha + \pi(TPI_d \times \text{Post}_t) + \gamma_d + \delta_t + u_{dt}$$

**Second stage (2SLS):** $\beta^{IV} = \beta^{RF} / \hat{\pi}$ — the causal effect of STR
penetration on housing outcomes. District fixed effects $\gamma_d$ absorb time-invariant district
characteristics; year fixed effects $\delta_t$ absorb common trends. Standard errors are clustered
at the district level.

> **Data availability note:** District-level STR listing counts required for the first stage
> ($\hat{\pi}$) and 2SLS ($\beta^{IV}$) have been formally requested from the Central Statistical
> Office of Saint Lucia but have not yet been received. All regression results below are therefore
> **reduced-form estimates** ($\beta^{RF}$). Full 2SLS estimates will be reported once listing
> data are received.

The exclusion restriction requires $TPI_d$ to affect housing outcomes *only through*
Airbnb-driven STR activity. The two most plausible threats are: (1) **concurrent hotel expansion**
in high-TPI districts, addressed by controlling for SLTA hotel room growth (2010–2022); and
(2) **pre-existing spatial trends**, tested via a pre-period placebo regression over 2001–2010
where $\hat{\beta}^{RF} \approx 0$ is required.

# Descriptive Statistics

## Table 1: District-Level Housing Outcomes, 2010 and 2022

```{r table-district-outcomes}
district_wide |>
  arrange(desc(tpi)) |>
  mutate(
    across(c(renter_rate_10, renter_rate_22, owner_rate_10, owner_rate_22),
           ~ . * 100),
    tourism_tier = factor(tourism_tier, levels = c("High", "Medium", "Low"))
  ) |>
  select(district, tpi,
         renter_rate_10, renter_rate_22, d_renter,
         owner_rate_10,  owner_rate_22,  d_owner,
         hh_size_10,     hh_size_22,     d_hh_size) |>
  kbl(
    digits  = c(0, 3, 1, 1, 1, 1, 1, 1, 2, 2, 2),
    col.names = c("District", "TPI (Share)",
                  "Renter 2010 (%)", "Renter 2022 (%)", "Δ Renter (pp)",
                  "Owner 2010 (%)",  "Owner 2022 (%)",  "Δ Owner (pp)",
                  "HH Size 2010",    "HH Size 2022",    "Δ HH Size"),
    caption = "Table 1. District-level housing outcomes, Saint Lucia 2010–2022. Districts ordered by pre-Airbnb tourism intensity (high to low). pp = percentage points. HH = household.",
    booktabs = TRUE, linesep = ""
  ) |>
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 8) |>
  add_header_above(c(" " = 2, "Renter Rate" = 3, "Ownership Rate" = 3, "Avg. HH Size" = 3)) |>
  footnote(
    general = "TPI = Tourism Proximity Index (district share of national hotel-room stock, 2010). Bold = high-TPI districts (TPI >= 0.20); italic = medium-TPI (0.09-0.20). Source: CSO Saint Lucia Population and Housing Census 2010, 2022; SLTA 2010.",
    general_title = "",
    footnote_as_chunk = TRUE,
    threeparttable = TRUE
  )
```

The raw data reveal a clear gradient: **high-tourism districts show the largest increases in renter
rates and the sharpest declines in homeownership** over the 2010–2022 period. This pattern is
consistent with the short-term rental conversion hypothesis — landlords in tourism-intensive
districts diverting units toward Airbnb, reducing the supply of long-term rentals and
owner-occupied housing accessible to residents.

## Figure 1: Renter Rates by District, 2010 vs. 2022

```{r fig-renter-rates, fig.cap="Figure 1. Renter Rate by District, 2010 vs. 2022. Districts ordered by TPI — Bartik share (bottom = highest TPI). Source: CSO Saint Lucia Population and Housing Census 2010, 2022. Weighted district-level estimates."}
district_wide |>
  arrange(tpi) |>
  mutate(district = factor(district, levels = district)) |>
  select(district, tpi, renter_rate_10, renter_rate_22) |>
  pivot_longer(c(renter_rate_10, renter_rate_22),
               names_to = "year",
               values_to = "renter_rate") |>
  mutate(
    year  = if_else(year == "renter_rate_10", "2010", "2022"),
    label = scales::percent(renter_rate, accuracy = 0.1)
  ) |>
  ggplot(aes(x = renter_rate, y = district, fill = year)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_text(aes(label = label),
            position = position_dodge(width = 0.7),
            hjust = -0.1, size = 2.5) +
  scale_x_continuous(labels = scales::percent,
                     expand = expansion(mult = c(0, 0.15))) +
  scale_fill_manual(values = c("2010" = "#D7191C", "2022" = "#FDAE61"),
                    name = "Census Year") +
  labs(
    title    = "Figure 1. Renter Rate by District, 2010 vs. 2022",
    subtitle = "Districts ordered by TPI — Bartik share (bottom = highest TPI)",
    x = "Share of Households Renting", y = NULL,
    caption  = "Source: CSO Saint Lucia Population and Housing Census 2010, 2022.\nWeighted district-level estimates."
  )
```

Figure 1 shows that renter rates increased between 2010 and 2022 in virtually every district, but
the increase was most pronounced in **Gros Islet and Soufrière** — the two districts with the
highest TPI. This visual pattern provides the first piece of evidence for the Bartik IV: the
districts that held the largest share of national tourism activity before Airbnb's arrival
experienced the sharpest housing market shifts after it.

# Preliminary Regression Results

## Figure 3: Tourism Intensity and the Change in Renter Rate, 2010–2022

```{r fig-scatter-renter, fig.cap="Figure 3. Pre-Airbnb Tourism Intensity vs. Change in Renter Rate. Each point is one district; regression line shows linear trend across all 10 districts. Source: CSO Saint Lucia Population and Housing Census 2010, 2022; Saint Lucia Tourism Authority Statistical Digest 2010."}
district_wide |>
  mutate(tourism_tier = factor(tourism_tier, levels = c("High", "Medium", "Low"))) |>
  ggplot(aes(x = tpi, y = d_renter, label = district,
             color = tourism_tier)) +
  geom_smooth(method = "lm", se = TRUE,
              color = "grey50", fill = "grey85", linewidth = 0.7) +
  geom_point(size = 3, alpha = 0.9) +
  geom_text_repel(size = 2.8, max.overlaps = 12, show.legend = FALSE) +
  scale_color_manual(values = c("High" = "#D7191C", "Medium" = "#FDAE61", "Low" = "#2C7BB6"),
                     name = "Tourism Tier") +
  labs(
    title    = "Figure 3. Pre–Airbnb Tourism Intensity vs. Change in Renter Rate",
    subtitle = "Each point is one district; regression line shows linear trend across all 10 districts",
    x        = "Tourism Proximity Index (TPI, 2010 share of national hotel stock)",
    y        = "Change in Renter Rate 2010–2022 (pct. points)",
    caption  = "Source: CSO Saint Lucia Population and Housing Census 2010, 2022;\nSaint Lucia Tourism Authority Statistical Digest 2010."
  )
```

Figure 3 presents the **key reduced-form relationship**: the change in renter rate between 2010 and
2022 plotted against pre-Airbnb tourism intensity. A positive slope would confirm that districts
more exposed to tourism — and hence more exposed to Airbnb after 2014 — shifted more strongly
toward renter-occupied tenure. The fitted regression line represents the continuous DiD relationship
underlying the estimates in Table 2.

## Figure 4: Monthly Rent by District, 2022 (Cross-Sectional)

```{r fig-rent-2022, fig.cap="Figure 4. Median Monthly Rent by District, 2022. Among renter-occupied households only; districts ordered by median rent. Source: CSO Saint Lucia Population and Housing Census 2022. N renters reporting valid rent: 5,791."}
hh_2022 |>
  filter(tenure %in% 7:8,
         !is.na(monthly_rent),
         monthly_rent > 0, monthly_rent < 99999) |>
  left_join(district_wide |> select(district, tourism_tier),
            by = "district") |>
  mutate(tourism_tier = factor(tourism_tier, levels = c("High", "Medium", "Low"))) |>
  group_by(district, tourism_tier) |>
  summarise(median_rent = median(rep(monthly_rent, times = round(hh_weight))),
            .groups = "drop") |>
  arrange(median_rent) |>
  mutate(district = factor(district, levels = district),
         label    = paste0("EC$", format(round(median_rent), big.mark = ","))) |>
  ggplot(aes(x = median_rent, y = district, fill = tourism_tier)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = label), hjust = -0.1, size = 2.8) +
  scale_x_continuous(labels = dollar_format(prefix = "EC$"),
                     expand = expansion(mult = c(0, 0.20))) +
  scale_fill_manual(values = c("High" = "#D7191C", "Medium" = "#FDAE61", "Low" = "#2C7BB6"),
                    name = "Tourism Tier") +
  labs(
    title   = "Figure 4. Median Monthly Rent by District, 2022",
    subtitle = "Among renter-occupied households only; districts ordered by median rent",
    x       = "Median Monthly Rent (EC$)", y = NULL,
    caption = "Source: CSO Saint Lucia Population and Housing Census 2022.\nN renters reporting valid rent: 5,791."
  )
```

Although a comparable rent variable is unavailable in the 2010 census, the 2022 cross-section in
Figure 4 documents substantial spatial variation in rent levels. High-tourism districts command the
highest median rents, consistent with a long-run market in which short-term rental platforms have
pushed up the floor price for rental accommodation.

# Discussion and Next Steps

## Summary of Preliminary Findings

Taken together, the descriptive and regression evidence from the 2010 and 2022 Saint Lucia censuses
tells a consistent story:

1. **Renter rates rose more steeply in high-tourism districts.** The largest increases in the share
   of renter-occupied households are concentrated in Gros Islet and Soufrière — the two districts
   most exposed to pre-existing tourism activity and hence to Airbnb post-2014.

2. **Homeownership declined most sharply in tourism-intensive areas.** The mirror decline in
   owner-occupied tenure in these districts suggests that the affordability barrier to ownership
   has widened, consistent with rising housing costs squeezing residents out of the buyer market.

3. **Household size and crowding dynamics reflect affordability pressure.** Changes in average
   household size and persons per bedroom in high-tourism districts may indicate that cost-burdened
   renters are consolidating into fewer, more crowded dwellings.

4. **2022 rent levels are highest in tourism-intensive districts.** While no comparable 2010 rent
   benchmark exists, the 2022 cross-section confirms that renters in Gros Islet and Soufrière pay
   substantially more than those in low-tourism districts.
