---
title: "Data Mining For Short Term Rentals Thesis"
author: "Mave Kimara Alexander"
format:
  pdf:
    pdf-engine: xelatex
    toc: true
    toc-depth: 3
    number-sections: true
geometry: margin=0.2in
editor: visual
execute:
  warning: false
  message: false
---

```{r}
library(haven)
library(tidyverse)
library(labelled)
```

## Loading Data

```{r}
Raw_Census_Data_2010 <- read_sav("person_house_merged.sav")
labels_table_2010 <- tibble(
  variable_name = names(Raw_Census_Data_2010),
  SPSS_variable_label = sapply(Raw_Census_Data_2010, function(x) {
    lab <- labelled::var_label(x)
    if (is.null(lab) || lab == "") NA_character_ else as.character(lab)
  }),
  SPSS_value_labels = sapply(Raw_Census_Data_2010, function(x) {
    vals <- labelled::val_labels(x)
    if (length(vals) == 0) NA_character_
    else paste(names(vals), vals, collapse = "; ")
  })
)

print(labels_table_2010, n = Inf, width = Inf)
```
```{r}
Raw_Census_Data_2010 |>
  count(DWELLING) |>
  arrange(DWELLING) |>
  print(n = Inf)
```
```{r}
summary(Raw_Census_Data_2010$DWELLING)

```
```{r}
Raw_Census_Data_2010 |>
  count(H11_TYPE) |>
  arrange(H11_TYPE) |>
  print(n = Inf)
```
```{r}
# ── Verify 2010 district codes match 2022 ────────────────────────────────────

# Check raw DISTRICT values in 2010
Raw_Census_Data_2010 |>
  count(DISTRICT) |>
  arrange(DISTRICT) |>
  print(n = Inf)

# Cross-check against DISTRICT2 (variable 101) — this may have the
# sub-Castries breakdown you need to match 2022's Castries 1/2/3
Raw_Census_Data_2010 |>
  count(DISTRICT, DISTRICT2) |>
  arrange(DISTRICT, DISTRICT2) |>
  print(n = Inf)

# Also check DISTRICTA and DISTRICTB (variables 190/191)
Raw_Census_Data_2010 |>
  count(DISTRICT, DISTRICTA, DISTRICTB) |>
  arrange(DISTRICT) |>
  print(n = Inf)
```
```{r}
# ── Create 2010 household-level unique ID ─────────────────────────────────────
# No CompositeKey in 2010 — construct from District + ED + HH
Raw_Census_Data_2010 <- Raw_Census_Data_2010 |>
  mutate(household_id_2010 = paste(DISTRICT, ED, HH, sep = "_"))

# ── Build 2010 Working Table ──────────────────────────────────────────────────
Thesis_Working_Data_2010 <- Raw_Census_Data_2010 |>
  distinct(household_id_2010, .keep_all = TRUE) |>
  select(
    household_id_2010,
    DISTRICT, poldist,
    NPERS,
    H11_TYPE, H13_OWN,
    H15_WALLS, H16_ROOF, H17_YR_BUILT,
    H18_WATER, H20_TOILET, H21_LIGHTING,
    H23_ROOMS, H24_BEDROOMS,
    H30_VEHICLES,
    HWEIGHT
  ) |>
  rename(
    household_id     = household_id_2010,
    district_raw     = DISTRICT,
    constituency     = poldist,
    household_size   = NPERS,
    building_type    = H11_TYPE,
    tenure_status    = H13_OWN,
    wall_material    = H15_WALLS,
    roof_material    = H16_ROOF,
    year_built       = H17_YR_BUILT,
    water_source     = H18_WATER,
    toilet_type      = H20_TOILET,
    lighting_source  = H21_LIGHTING,
    rooms            = H23_ROOMS,
    bedrooms         = H24_BEDROOMS,
    vehicles_owned   = H30_VEHICLES,
    household_weight = HWEIGHT
  ) |>
  zap_labels() |>
  mutate(
    # ── District mapping confirmed from output ────────────────────────────────
    # DISTRICT 1 = Castries City    → matches 2022 "Castries 1"
    # DISTRICT 2 = Castries Suburban → matches 2022 "Castries 2"  
    # DISTRICT 3 = Castries Rural   → matches 2022 "Castries 3"
    # Districts 4–12 map 1:1 with 2022
    # NOTE: Confirm Castries 1/2/3 labelling with Statistics Office
    district = case_when(
      district_raw == 1  ~ "Castries 1",
      district_raw == 2  ~ "Castries 2",
      district_raw == 3  ~ "Castries 3",
      district_raw == 4  ~ "Anse La Raye",
      district_raw == 5  ~ "Canaries",
      district_raw == 6  ~ "Soufriere",
      district_raw == 7  ~ "Choiseul",
      district_raw == 8  ~ "Laborie",
      district_raw == 9  ~ "Vieux Fort",
      district_raw == 10 ~ "Micoud",
      district_raw == 11 ~ "Dennery",
      district_raw == 12 ~ "Gros Islet",
      TRUE               ~ paste0("Unknown (", district_raw, ")")
    ),
    # ── Tenure mapping for 2010 ───────────────────────────────────────────────
    # H13_OWN: 1=Owned fully, 2=Owned with mortgage, 3=Rented-private,
    #          4=Rented-government, 5=Rent free, 6=Other
    # Owner-occupied = 1 or 2 (matches 2022 codes 1-4)
    # Long-term rental = 3 or 4 (matches 2022 codes 7,8,10)
    owner_occupied    = if_else(tenure_status %in% c(1, 2), 1, 0),
    long_term_rental  = if_else(tenure_status %in% c(3, 4), 1, 0),
    # ── Clean missing values ──────────────────────────────────────────────────
    across(
      c(household_size, building_type, tenure_status, wall_material,
        roof_material, year_built, water_source, toilet_type,
        lighting_source, rooms, bedrooms, vehicles_owned),
      ~ if_else(. %in% c(-999999999, 999999999, 99, 999, 9), 
                NA_real_, as.numeric(.))
    ),
    # ── Housing quality indicators (same definitions as 2022) ─────────────────
    piped_water    = if_else(water_source %in% c(1, 2), 1, 0),
    electricity    = if_else(lighting_source == 1, 1, 0),
    improved_toilet = if_else(toilet_type %in% c(1, 2, 3), 1, 0),
    durable_walls  = if_else(wall_material %in% c(1, 2, 3), 1, 0),
    durable_roof   = if_else(roof_material %in% c(1, 2, 3), 1, 0),
    # ── Crowding indicators ───────────────────────────────────────────────────
    rooms_clean    = if_else(rooms > 0, rooms, NA_real_),
    bedrooms_clean = if_else(bedrooms > 0, bedrooms, NA_real_),
    persons_per_room    = household_size / rooms_clean,
    persons_per_bedroom = household_size / bedrooms_clean,
    overcrowded    = if_else(persons_per_bedroom > 2, 1, 0),
    # ── Spare bedroom capacity ────────────────────────────────────────────────
    spare_bedrooms = bedrooms_clean - household_size,
    # ── Hosting suitability (pre-treatment instrument) ────────────────────────
    hosting_suitable = if_else(
      spare_bedrooms > 0 &
      piped_water == 1 &
      electricity == 1 &
      improved_toilet == 1,
      1, 0
    ),
    census_year = 2010
  ) |>
  filter(!is.na(district))

# ── Verify row counts look reasonable ────────────────────────────────────────
Thesis_Working_Data_2010 |>
  count(district) |>
  arrange(district)
```

```{r}
# ── 2010 District-Level Summaries ─────────────────────────────────────────────

# 1. Rental Supply
Rental_supply_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    long_term_rentals = sum(long_term_rental * household_weight, na.rm = TRUE),
    total_households  = sum(household_weight, na.rm = TRUE),
    rental_share      = long_term_rentals / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(long_term_rentals))

# 2. Homeownership
Homeownership_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    owner_households  = sum(owner_occupied * household_weight, na.rm = TRUE),
    total_households  = sum(household_weight, na.rm = TRUE),
    homeownership_rate = owner_households / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(homeownership_rate))

# 3. Crowding
Crowding_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    avg_persons_per_room    = weighted.mean(persons_per_room, household_weight, 
                                            na.rm = TRUE),
    avg_persons_per_bedroom = weighted.mean(persons_per_bedroom, household_weight, 
                                            na.rm = TRUE),
    overcrowding_rate       = weighted.mean(overcrowded, household_weight, 
                                            na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(overcrowding_rate))

# 4. Spare Bedrooms
Spare_bedrooms_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    avg_spare_bedrooms = weighted.mean(spare_bedrooms, household_weight, 
                                       na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(avg_spare_bedrooms))

# 5. Housing Quality
Housing_quality_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    piped_water_rate     = weighted.mean(piped_water, household_weight, 
                                         na.rm = TRUE),
    electricity_rate     = weighted.mean(electricity, household_weight, 
                                         na.rm = TRUE),
    improved_toilet_rate = weighted.mean(improved_toilet, household_weight, 
                                         na.rm = TRUE),
    durable_walls_rate   = weighted.mean(durable_walls, household_weight, 
                                         na.rm = TRUE),
    durable_roof_rate    = weighted.mean(durable_roof, household_weight, 
                                         na.rm = TRUE),
    avg_vehicles         = weighted.mean(vehicles_owned, household_weight, 
                                         na.rm = TRUE),
    .groups = "drop"
  )

# 6. Hosting Suitability Index (this is your pre-treatment instrument)
Suitability_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    suitability_index      = weighted.mean(hosting_suitable, household_weight, 
                                           na.rm = TRUE),
    suitable_hh_estimated  = sum(hosting_suitable * household_weight, 
                                 na.rm = TRUE),
    total_households       = sum(household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(suitability_index))

# ── Combined 2010 District Summary Table ─────────────────────────────────────
District_Summary_2010 <- Rental_supply_2010 |>
  select(district, total_households, rental_share) |>
  left_join(Homeownership_2010  |> select(district, homeownership_rate), 
            by = "district") |>
  left_join(Crowding_2010       |> select(district, overcrowding_rate), 
            by = "district") |>
  left_join(Suitability_2010    |> select(district, suitability_index), 
            by = "district") |>
  mutate(census_year = 2010)

# ── Combined 2022 District Summary Table (same structure) ────────────────────
District_Summary_2022 <- Rental_supply_per_district |>
  select(district, total_households, rental_share) |>
  left_join(Homeownership_per_district |> select(district, homeownership_rate), 
            by = "district") |>
  left_join(Crowding_per_district      |> select(district, overcrowding_rate), 
            by = "district") |>
  left_join(Suitability_by_district    |> select(district, suitability_index), 
            by = "district") |>
  mutate(census_year = 2022)

# ── Stack into Panel ──────────────────────────────────────────────────────────
District_Panel <- bind_rows(District_Summary_2010, District_Summary_2022) |>
  arrange(district, census_year)

# ── Before/After Comparison Table ────────────────────────────────────────────
District_Panel |>
  mutate(
    total_households   = comma(round(total_households)),
    rental_share       = percent(rental_share, accuracy = 0.1),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1),
    overcrowding_rate  = percent(overcrowding_rate, accuracy = 0.1),
    suitability_index  = percent(suitability_index, accuracy = 0.1)
  ) |>
  select(district, census_year, total_households, rental_share, 
         homeownership_rate, overcrowding_rate, suitability_index) |>
  kbl(
    booktabs = TRUE,
    caption  = "District Housing Indicators: 2010 vs 2022",
    col.names = c("District", "Year", "Total HH", "Rental Share", 
                  "Ownership Rate", "Overcrowding", "Suitability"),
    align = c("l","c","r","r","r","r","r")
  ) |>
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"), 
    font_size = 8
  ) |>
  collapse_rows(columns = 1, valign = "middle")
```


```{r}
Raw_Census_Data <- read_sav("PersonHHoldMerge 2022 Annon.sav")
```

# Column Labels

```{r}
labels_table <- tibble(
  variable_name = names(Raw_Census_Data),

  SPSS_variable_label = sapply(Raw_Census_Data, function(x) {
    lab <- labelled::var_label(x)
    if (is.null(lab) || lab == "") NA_character_ else as.character(lab)
  }),

  SPSS_value_labels = sapply(Raw_Census_Data, function(x) {
    vals <- labelled::val_labels(x)
    if (length(vals) == 0) {
      NA_character_
    } else {
      paste(names(vals), vals, collapse = "; ")
    }
  })
)

print(labels_table, n = Inf, width = Inf)
```

**The codebook shows that dwell_status is a dwelling-level variable with categories including AirBNB. It is not available in the current dataset. I am awaiting a reply from the Statistics Office.**

# Creating Working Table

```{r}
Thesis_Working_Data <- Raw_Census_Data |>
  distinct(CompositeKey, .keep_all = TRUE) |>
  select(
    CompositeKey,
    DISTRICT_ID,
    CONSTITUENCY,
    num_males,
    num_females,
    Npersons,
    h2_1,
    h2_3a,
    h2_3b1,
    h2_3b2,
    h2_5,
    h2_6,
    h2_7,
    h2_8,
    h2_11a,
    h2_12,
    h2_14,
    h2_15,
    h2_21,
    HHLD_WEIGHT
  )
```

# Working Data Labels

```{r}
working_data_labels <- tibble(
  variable = names(Thesis_Working_Data),
  variable_label = sapply(Thesis_Working_Data, function(x) {
    lab <- attr(x, "label")
    if (is.null(lab)) NA_character_ else as.character(lab)
  }),
  value_labels = sapply(Thesis_Working_Data, function(x) {
    vals <- attr(x, "labels")
    if (is.null(vals)) NA_character_
    else paste(names(vals), vals, collapse = "; ")
  })
)

print(working_data_labels, n = Inf, width = Inf)
```

# Rename and Clean Columns

```{r}
Thesis_Working_Data <- Thesis_Working_Data |>
  rename(
    household_id   = CompositeKey,
    district       = DISTRICT_ID,
    constituency   = CONSTITUENCY,
    males          = num_males,
    females        = num_females,
    household_size = Npersons,
    building_type  = h2_1,
    tenure_status  = h2_3a,
    monthly_rent   = h2_3b1,
    rent_furnishing = h2_3b2,
    roof_material  = h2_5,
    wall_material  = h2_6,
    year_built     = h2_7,
    water_source   = h2_8,
    toilet_type    = h2_11a,
    lighting_source = h2_12,
    rooms          = h2_14,
    bedrooms       = h2_15,
    vehicles_owned = h2_21,
    household_weight = HHLD_WEIGHT
  )
```

```{r}
Thesis_Working_Data <- Thesis_Working_Data |>
  zap_labels() |>
  mutate(
    district = case_when(
      district == 1  ~ "Castries 1",
      district == 2  ~ "Castries 2",
      district == 3  ~ "Castries 3",
      district == 4  ~ "Anse La Raye",
      district == 5  ~ "Canaries",
      district == 6  ~ "Soufriere",
      district == 7  ~ "Choiseul",
      district == 8  ~ "Laborie",
      district == 9  ~ "Vieux Fort",
      district == 10 ~ "Micoud",
      district == 11 ~ "Dennery",
      district == 12 ~ "Gros Islet",
      TRUE           ~ as.character(district)
    ),
    monthly_rent = as.numeric(monthly_rent),
    across(
      c(males, females, household_size, monthly_rent, rooms, bedrooms,
        vehicles_owned, roof_material, wall_material, year_built,
        water_source, toilet_type, lighting_source, tenure_status,
        building_type),
      ~ if_else(. == -999999999, NA_real_, as.numeric(.))
    )
  )
```

**Note on district codes:** Districts 1, 2, and 3 are believed to be subdivisions of Castries, the capital. This will be confirmed with the Statistics Office.

## Reference Table

```{r}
labels_reference <- tibble(
  variable = names(Thesis_Working_Data),
  description = c(
    "Household unique identifier",
    "Administrative district",
    "Electoral constituency",
    "Number of male household members",
    "Number of female household members",
    "Total persons in household",
    "Type of building structure",
    "Housing tenure status",
    "Monthly rent paid",
    "Rental furnishing status",
    "Roof material",
    "Wall material",
    "Year dwelling constructed",
    "Main water source",
    "Type of toilet facility",
    "Main lighting source",
    "Total number of rooms",
    "Number of bedrooms",
    "Number of vehicles owned",
    "Survey household weight"
  )
)

labels_reference
```

# Short Term Rentals Per District

**The dwell_status variable (Short-Term Occupation = 8, AirBNB = 12) has been requested from the Statistics Office and will be incorporated once received.**

Short-term rentals are conceptually defined as dwellings classified in the census dwelling-status variable as either **Short-Term Occupation (code 8)** or **AirBNB (code 12)**.

A binary indicator $STR_i$ is defined as:

$$
STR_i =
\begin{cases}
1 & \text{if } dwell\_status_i \in \{8,12\} \\
0 & \text{otherwise}
\end{cases}
$$

The number of short-term rentals in district $d$ is calculated as the weighted sum:

$$
STR_d = \sum_{i \in d} STR_i \times w_i
$$

where $i$ indexes individual dwellings and $w_i$ represents the household survey weight.

# Rental Supply by District

```{r}
# Tenure status codes: 7 = Renting unfurnished, 8 = Renting furnished, 10 = Rent free
Thesis_Working_Data <- Thesis_Working_Data |>
  mutate(
    long_term_rental = if_else(tenure_status %in% c(7, 8, 10), 1, 0)
  )

Rental_supply_per_district <- Thesis_Working_Data |>
  group_by(district) |>
  summarise(
    long_term_rentals = sum(long_term_rental * household_weight, na.rm = TRUE),
    total_households  = sum(household_weight, na.rm = TRUE),
    rental_share      = long_term_rentals / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(long_term_rentals))

Rental_supply_per_district
```

# Average Price of Long Term Rentals per District

```{r}
Rent_per_district <- Thesis_Working_Data |>
  filter(
    tenure_status %in% c(7, 8, 10),
    !is.na(monthly_rent),
    monthly_rent > 0,
    monthly_rent < 99999   
  ) |>
  group_by(district) |>
  summarise(
    avg_monthly_rent    = weighted.mean(monthly_rent, household_weight, na.rm = TRUE),
    renting_households  = sum(household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(avg_monthly_rent))

Rent_per_district
```

# Home Ownership Rates by District

```{r}
# Tenure status codes: 1 = Owned fully (jointly), 2 = Owned fully by male,
# 3 = Owned fully by female, 4 = Owned (mortgaged)
Thesis_Working_Data <- Thesis_Working_Data |>
  mutate(
    owner_occupied = if_else(tenure_status %in% c(1, 2, 3, 4), 1, 0)
  )

Homeownership_per_district <- Thesis_Working_Data |>
  group_by(district) |>
  summarise(
    owner_households   = sum(owner_occupied * household_weight, na.rm = TRUE),
    total_households   = sum(household_weight, na.rm = TRUE),
    homeownership_rate = owner_households / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(homeownership_rate))

Homeownership_per_district
```

# Household Crowding Indicators

```{r}
Thesis_Working_Data <- Thesis_Working_Data |>
  mutate(
    rooms_clean    = if_else(rooms    > 0, rooms,    NA_real_),
    bedrooms_clean = if_else(bedrooms > 0, bedrooms, NA_real_),
    persons_per_room    = household_size / rooms_clean,
    persons_per_bedroom = household_size / bedrooms_clean,
    overcrowded = if_else(persons_per_bedroom > 2, 1, 0)
  )
```

# Crowding per District

```{r}
Crowding_per_district <- Thesis_Working_Data |>
  group_by(district) |>
  summarise(
    avg_persons_per_room    = weighted.mean(persons_per_room,    household_weight, na.rm = TRUE),
    avg_persons_per_bedroom = weighted.mean(persons_per_bedroom, household_weight, na.rm = TRUE),
    overcrowding_rate       = weighted.mean(overcrowded,         household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(overcrowding_rate))

Crowding_per_district
```

# Spare Bedroom Capacity

```{r}
Thesis_Working_Data <- Thesis_Working_Data |>
  mutate(
    spare_bedrooms = bedrooms_clean - household_size
  )

Spare_bedrooms_per_district <- Thesis_Working_Data |>
  group_by(district) |>
  summarise(
    avg_spare_bedrooms = weighted.mean(spare_bedrooms, household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(avg_spare_bedrooms))

Spare_bedrooms_per_district
```

# Housing Quality Indicators

```{r}
# Value label reference (from codebook):
# water_source: 1 = Public piped into dwelling, 2 = Public piped into yard
# lighting_source: 1 = Electricity - Public
# toilet_type: 1 = WC flush to sewer, 2 = WC flush to septic, 3 = WC flush to pit
# wall_material: 1 = Wood, 2 = Concrete/Concrete Blocks, 3 = Wood and Concrete
# roof_material: 1 = Sheet metal, 2 = Shingle (asphalt), 3 = Shingle (wood)

Thesis_Working_Data <- Thesis_Working_Data |>
  mutate(
    piped_water    = if_else(water_source   %in% c(1, 2),    1, 0),
    electricity    = if_else(lighting_source == 1,            1, 0),
    improved_toilet = if_else(toilet_type   %in% c(1, 2, 3), 1, 0),
    durable_walls  = if_else(wall_material  %in% c(1, 2, 3), 1, 0),
    durable_roof   = if_else(roof_material  %in% c(1, 2, 3), 1, 0)
  )
```

# Housing Quality per District

```{r}
Housing_quality_per_district <- Thesis_Working_Data |>
  group_by(district) |>
  summarise(
    piped_water_rate     = weighted.mean(piped_water,     household_weight, na.rm = TRUE),
    electricity_rate     = weighted.mean(electricity,     household_weight, na.rm = TRUE),
    improved_toilet_rate = weighted.mean(improved_toilet, household_weight, na.rm = TRUE),
    durable_walls_rate   = weighted.mean(durable_walls,   household_weight, na.rm = TRUE),
    durable_roof_rate    = weighted.mean(durable_roof,    household_weight, na.rm = TRUE),
    avg_vehicles         = weighted.mean(vehicles_owned,  household_weight, na.rm = TRUE),
    .groups = "drop"
  )

Housing_quality_per_district
```

\pagebreak

# Housing Age by District

```{r}
# year_built is stored as a categorical period code (e.g., 1 = Before 1980,
# 2 = 1980-1989, etc.) so the weighted mean gives a period index, not a year.
# Treat as ordinal index: higher = more recently built.
Year_built_per_district <- Thesis_Working_Data |>
  filter(!is.na(year_built)) |>
  group_by(district) |>
  summarise(
    avg_year_built_index = weighted.mean(year_built, household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(avg_year_built_index))

Year_built_per_district
```

# Hosting Suitability Index

This index captures each district's baseline capacity to host short-term rentals, using pre-treatment housing characteristics available in the 2022 census. It will serve as the treatment intensity variable in the cross-sectional analysis, and as a pre-treatment covariate if 2010 data becomes available.

```{r}
# A household is considered hosting-suitable if it has:
# - At least one spare bedroom (bedrooms > household size)
# - Piped water access
# - Public electricity
# - An improved toilet
Thesis_Working_Data <- Thesis_Working_Data |>
  mutate(
    hosting_suitable = if_else(
      spare_bedrooms > 0 &
        piped_water   == 1 &
        electricity   == 1 &
        improved_toilet == 1,
      1, 0
    )
  )

Suitability_by_district <- Thesis_Working_Data |>
  group_by(district) |>
  summarise(
    suitability_index     = weighted.mean(hosting_suitable, household_weight, na.rm = TRUE),
    suitable_hh_estimated = sum(hosting_suitable * household_weight, na.rm = TRUE),
    total_households      = sum(household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(suitability_index))

Suitability_by_district
```

\pagebreak

# District Summary

```{r}
District_Analysis_Table <- Rental_supply_per_district |>
  select(district, long_term_rentals, total_households, rental_share) |>
  left_join(Rent_per_district        |> select(district, avg_monthly_rent, renting_households),  by = "district") |>
  left_join(Homeownership_per_district |> select(district, owner_households, homeownership_rate), by = "district") |>
  left_join(Crowding_per_district    |> select(district, avg_persons_per_room, avg_persons_per_bedroom, overcrowding_rate), by = "district") |>
  left_join(Spare_bedrooms_per_district |> select(district, avg_spare_bedrooms),                  by = "district") |>
  left_join(Housing_quality_per_district |> select(district, piped_water_rate, electricity_rate,
              improved_toilet_rate, durable_walls_rate, durable_roof_rate, avg_vehicles),          by = "district") |>
  left_join(Year_built_per_district  |> select(district, avg_year_built_index),                   by = "district") |>
  left_join(Suitability_by_district  |> select(district, suitability_index),                      by = "district") |>
  arrange(desc(total_households))

District_Analysis_Table
```

\pagebreak

# Potential Treatments for Thesis

## Expansion of Short-Term Rental Platforms (Technology Shock)

One possible treatment could be the global expansion of short-term rental platforms such as Airbnb after around 2014, which may have made it easier for homeowners to rent rooms or entire homes to tourists. Although the platform became available across Saint Lucia at roughly the same time, districts may have been affected differently depending on their housing characteristics. The treatment could therefore be defined as districts with higher hosting suitability in 2010, such as those with more spare bedrooms, higher internet access, or closer proximity to tourism areas. These districts may have been more likely to adopt short-term rentals once the platforms became widely used, which could possibly lead to housing market effects such as higher rents, reduced owner-occupancy, or changes in housing supply.

## Expansion of International Airlift (Tourism Demand Shock)

Another possible treatment could be increases in international flight routes to Saint Lucia between roughly 2015 and 2021. New nonstop flights may have increased the number of visitors arriving on the island, which could raise demand for short-term accommodation outside traditional hotels. Although the additional flights affect the whole country, districts closer to tourism infrastructure may experience stronger effects. The treatment could therefore be defined as districts with higher baseline tourism exposure, such as areas near beaches, resorts, or established tourism zones. These districts may experience stronger growth in short-term rentals as visitor demand increases, which could potentially influence housing prices and housing availability.

## Tourism Investment Incentives and Real Estate Development (Housing Supply Shock)

A third possible treatment could be government policies that encouraged tourism-related real estate development. The Tourism Stimulus and Investment Act (2014) introduced tax concessions to encourage investment in villas, condominiums, and luxury tourism developments, and the Citizenship by Investment Act (2015) introduced additional incentives for foreign investment in approved real estate projects. These policies apply nationally but may affect housing markets unevenly depending on where tourism-related development occurs. The treatment could therefore be defined as districts located near tourism-oriented developments or investment projects after these policies were introduced, where the incentives may have increased the supply of properties that could potentially be used as short-term rentals.

# Contingency Plan

If the dwell_status variable cannot be obtained from the Saint Lucia Central Statistics Office before the project deadline, the analysis could be reframed around housing market outcomes already available in the 2022 census, specifically average monthly rent and homeownership rates by district. Instead of using STR density as the outcome, these measures could serve as proxies for housing market pressure linked to the expansion of short-term rental platforms. The hosting suitability index could potentially be used as an instrumental variable for STR adoption, since districts with more suitable housing stock, spare bedrooms, piped water, electricity, and improved sanitation, may have been more likely to adopt short-term rentals once platforms like Airbnb became widely available after 2014. These housing characteristics were also determined well before the platform shock, which may help satisfy the exclusion restriction. If the number of districts proves too small for reliable estimation, the analysis could be conducted at the constituency level instead to improve statistical power. Under this contingency, the paper would be framed as a prospective research design
