---
title: "Data Mining For Short-Term Rentals: Housing Market Effects in Saint Lucia"
subtitle: "Evidence from the 2010 and 2022 Population and Housing Censuses"
author: "Mave Kimara Alexander | 113077424"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    code-fold: true
    code-summary: "Show code"
    theme: cosmo
    fig-width: 8
    fig-height: 5
    df-print: kable
    embed-resources: true
  pdf:
    toc: true
    number-sections: true
    fig-width: 7
    fig-height: 4.5
    geometry: margin=1in
    fontsize: 11pt
execute:
  warning: false
  message: false
  echo: true
bibliography: references.bib
---

```{r setup}
#| include: false
library(haven)
library(tidyverse)
library(labelled)
library(kableExtra)
library(scales)
library(ggrepel)
library(fixest)      # for feols() fixed-effects OLS
library(broom)       # for tidy() on regression objects
library(modelsummary) # for regression tables

theme_set(
  theme_minimal(base_size = 10) +
  theme(
    plot.title    = element_text(face = "bold", size = 11),
    plot.subtitle = element_text(size = 9, color = "grey40"),
    plot.caption  = element_text(size = 7, color = "grey50"),
    axis.text     = element_text(size = 8),
    legend.position = "bottom",
    legend.text   = element_text(size = 8)
  )
)

caption_2010 <- "Source: Saint Lucia Population and Housing Census 2010"
caption_2022 <- "Source: Saint Lucia Population and Housing Census 2022"
caption_both <- "Sources: Saint Lucia Population and Housing Census 2010 & 2022"
```

# Introduction

This study examines whether the expansion of short-term rental (STR) platforms and associated tourism investment incentives after 2014 affected housing market outcomes in Saint Lucia. Specifically, I ask: **did districts more capable of hosting short-term rentals experience greater increases in rents, larger declines in long-term rental supply, and higher household crowding between 2010 and 2022?**

The analysis exploits variation in pre-existing housing suitability across Saint Lucia's 12 administrative districts as a proxy for differential STR adoption intensity. Using data from the 2010 and 2022 Population and Housing Censuses, I construct a difference-in-differences (DiD) panel where districts with greater hosting capacity in 2010—measured by spare bedroom availability, piped water, electricity, and sanitation—are treated as higher-intensity adopters of the STR market that emerged after platforms like Airbnb became widely available around 2014.

## Research Question

> Do districts with greater pre-existing STR hosting suitability exhibit larger housing market changes — higher rents, lower homeownership, reduced long-term rental supply, and increased crowding — between 2010 and 2022?

## Identification Strategy

The core challenge is that STR adoption is endogenous to housing market conditions. Districts with high rents or low vacancy rates may attract more STR operators, creating reverse causality. To address this, I use the **2010 Hosting Suitability Index** as a pre-determined measure of treatment intensity. This index captures structural housing characteristics that existed before the STR platform shock (post-2014), making it plausibly exogenous to post-2014 changes in rental demand.

The estimating equation is:

$$Y_{dt} = \alpha_d + \gamma_t + \beta (\text{Suitability}_{d,2010} \times \text{Post}_t) + \varepsilon_{dt}$$

where:

-   $Y_{dt}$ is a housing outcome (rental share, homeownership rate, or overcrowding rate) in district $d$ at time $t$
-   $\alpha_d$ are district fixed effects absorbing all time-invariant district characteristics
-   $\gamma_t$ is a period fixed effect (2010 vs. 2022) absorbing common shocks
-   $\text{Suitability}_{d,2010}$ is the district's 2010 hosting suitability index, held fixed at its pre-treatment value
-   $\text{Post}_t = 1$ if $t = 2022$
-   $\beta$ is the coefficient of interest: the differential change in outcomes for districts with higher pre-treatment suitability

**Key assumption (parallel trends):** In the absence of STR platform expansion, high- and low-suitability districts would have followed similar trends in housing outcomes between 2010 and 2022. This is supported by the fact that these districts share the same national economy, legal framework, and macroeconomic shocks. The suitability index captures physical housing stock characteristics (bedrooms, utilities) rather than pre-existing demand pressures.

**Limitation:** With only 12 districts and 2 time periods (24 observations), statistical power is limited. Results should be interpreted as suggestive evidence of directional effects, not precise causal estimates. A constituency-level analysis (17 units) is presented as a robustness check.

::: callout-note
**Note on STR variable:** The `dwell_status` variable (Short-Term Occupation = 8, Airbnb = 12) has been requested from the Saint Lucia Central Statistics Office. Until it is received, the analysis uses the 2010 Hosting Suitability Index as treatment intensity and long-term rental share, homeownership, and crowding as outcome proxies for housing market pressure. See the Contingency Plan section.
:::

------------------------------------------------------------------------

# 2010 Census Data

## Loading 2010 Data

```{r load-2010}
Raw_Census_Data_2010 <- read_sav("person_house_merged.sav")
```

## 2010 Column Labels

```{r labels-2010}
labels_table_2010 <- tibble(
  variable_name       = names(Raw_Census_Data_2010),
  SPSS_variable_label = sapply(Raw_Census_Data_2010, function(x) {
    lab <- labelled::var_label(x)
    if (is.null(lab) || lab == "") NA_character_ else as.character(lab)
  }),
  SPSS_value_labels   = sapply(Raw_Census_Data_2010, function(x) {
    vals <- labelled::val_labels(x)
    if (length(vals) == 0) NA_character_
    else paste(names(vals), vals, collapse = "; ")
  })
)

print(labels_table_2010, n = Inf, width = Inf)
```

## 2010 District & Dwelling Checks

```{r checks-2010}
# Dwelling type distribution
Raw_Census_Data_2010 |>
  count(DWELLING) |>
  arrange(DWELLING) |>
  print(n = Inf)

# Building type distribution
Raw_Census_Data_2010 |>
  count(H11_TYPE) |>
  arrange(H11_TYPE) |>
  print(n = Inf)
```

## 2010 District Code Verification

```{r district-verify-2010}
Raw_Census_Data_2010 |>
  count(DISTRICT) |>
  arrange(DISTRICT) |>
  print(n = Inf)

Raw_Census_Data_2010 |>
  count(DISTRICT, DISTRICT2) |>
  arrange(DISTRICT, DISTRICT2) |>
  print(n = Inf)

Raw_Census_Data_2010 |>
  count(DISTRICT, DISTRICTA, DISTRICTB) |>
  arrange(DISTRICT) |>
  print(n = Inf)
```

## Creating 2010 Working Table

```{r working-table-2010}
Raw_Census_Data_2010 <- Raw_Census_Data_2010 |>
  mutate(household_id_2010 = paste(DISTRICT, ED, HH, sep = "_"))

Thesis_Working_Data_2010 <- Raw_Census_Data_2010 |>
  distinct(household_id_2010, .keep_all = TRUE) |>
  select(
    household_id_2010,
    DISTRICT, poldist,
    NPERS,
    H11_TYPE, H13_OWN,
    H15_WALLS, H16_ROOF, H17_YR_BUILT,
    H18_WATER, H20_TOILET, H21_LIGHTING,
    H23_ROOMS, H24_BEDROOMS,
    H30_VEHICLES,
    HWEIGHT
  ) |>
  rename(
    household_id      = household_id_2010,
    district_raw      = DISTRICT,
    constituency      = poldist,
    household_size    = NPERS,
    building_type     = H11_TYPE,
    tenure_status     = H13_OWN,
    wall_material     = H15_WALLS,
    roof_material     = H16_ROOF,
    year_built        = H17_YR_BUILT,
    water_source      = H18_WATER,
    toilet_type       = H20_TOILET,
    lighting_source   = H21_LIGHTING,
    rooms             = H23_ROOMS,
    bedrooms          = H24_BEDROOMS,
    vehicles_owned    = H30_VEHICLES,
    household_weight  = HWEIGHT
  ) |>
  zap_labels() |>
  mutate(
    district = case_when(
      district_raw == 1  ~ "Castries 1",
      district_raw == 2  ~ "Castries 2",
      district_raw == 3  ~ "Castries 3",
      district_raw == 4  ~ "Anse La Raye",
      district_raw == 5  ~ "Canaries",
      district_raw == 6  ~ "Soufriere",
      district_raw == 7  ~ "Choiseul",
      district_raw == 8  ~ "Laborie",
      district_raw == 9  ~ "Vieux Fort",
      district_raw == 10 ~ "Micoud",
      district_raw == 11 ~ "Dennery",
      district_raw == 12 ~ "Gros Islet",
      TRUE               ~ paste0("Unknown (", district_raw, ")")
    ),
    owner_occupied    = if_else(tenure_status %in% c(1, 2), 1, 0),
    long_term_rental  = if_else(tenure_status %in% c(3, 4), 1, 0),
    # --- FIX: clean ALL sentinel/missing codes for 2010 ---
    # 2010 uses 99/999/9999 for Not Stated in addition to the large sentinels
    across(
      c(household_size, building_type, tenure_status, wall_material,
        roof_material, year_built, water_source, toilet_type,
        lighting_source, rooms, bedrooms, vehicles_owned),
      ~ if_else(. %in% c(-999999999, 999999999, 99, 999, 9999, 9),
                NA_real_, as.numeric(.))
    ),
    # Housing quality indicators (same coding scheme as 2022)
    # water_source: 1=Public piped into dwelling, 2=Public piped into yard
    piped_water      = if_else(water_source %in% c(1, 2), 1, 0),
    # lighting_source: 1=Electricity – Public
    electricity      = if_else(lighting_source == 1, 1, 0),
    # toilet_type: 1=WC flush sewer, 2=WC flush septic, 3=WC flush pit
    improved_toilet  = if_else(toilet_type %in% c(1, 2, 3), 1, 0),
    # wall_material: 1=Wood, 2=Concrete/Blocks, 3=Wood and Concrete
    durable_walls    = if_else(wall_material %in% c(1, 2, 3), 1, 0),
    # roof_material: 1=Sheet metal, 2=Shingle asphalt, 3=Shingle wood
    durable_roof     = if_else(roof_material %in% c(1, 2, 3), 1, 0),
    # Crowding
    rooms_clean          = if_else(rooms > 0, rooms, NA_real_),
    bedrooms_clean       = if_else(bedrooms > 0, bedrooms, NA_real_),
    persons_per_room     = household_size / rooms_clean,
    persons_per_bedroom  = household_size / bedrooms_clean,
    overcrowded          = if_else(persons_per_bedroom > 2, 1, 0),
    # Spare bedroom capacity
    spare_bedrooms   = bedrooms_clean - household_size,
    # Hosting suitability: spare bedroom + piped water + electricity + improved toilet
    hosting_suitable = if_else(
      spare_bedrooms > 0 &
      piped_water    == 1 &
      electricity    == 1 &
      improved_toilet == 1,
      1, 0
    ),
    census_year = 2010L
  ) |>
  filter(!is.na(district))

Thesis_Working_Data_2010 |>
  count(district) |>
  arrange(district)
```

::: callout-important
**Fix applied:** The 2010 suitability index was returning `NA` in the original code because the housing quality variables (piped water, toilet, walls, roof) were coded with value `9` for "Not Stated" in the 2010 SPSS file. This was not caught by the original `NA` cleaning step which only filtered the large sentinel values. The updated cleaning step now explicitly converts `9`, `99`, `999`, and `9999` to `NA` before computing indicators. The suitability index should now be non-missing for districts with sufficient valid responses.
:::

## 2010 District-Level Summaries

### Rental Supply (2010)

```{r rental-supply-2010}
Rental_supply_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    long_term_rentals = sum(long_term_rental * household_weight, na.rm = TRUE),
    total_households  = sum(household_weight, na.rm = TRUE),
    rental_share      = long_term_rentals / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(long_term_rentals))

Rental_supply_2010 |>
  mutate(
    long_term_rentals = comma(round(long_term_rentals)),
    total_households  = comma(round(total_households)),
    rental_share      = percent(rental_share, accuracy = 0.1)
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Long-Term Rental Supply by District — 2010 (Weighted)",
    col.names = c("District", "Long-Term Rentals", "Total Households", "Rental Share"),
    align    = c("l", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)
```

### Homeownership (2010)

```{r homeownership-2010}
Homeownership_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    owner_households   = sum(owner_occupied * household_weight, na.rm = TRUE),
    total_households   = sum(household_weight, na.rm = TRUE),
    homeownership_rate = owner_households / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(homeownership_rate))

Homeownership_2010 |>
  mutate(
    owner_households   = comma(round(owner_households)),
    total_households   = comma(round(total_households)),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1)
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Home Ownership Rates by District — 2010 (Weighted)",
    col.names = c("District", "Owner Households", "Total Households", "Ownership Rate"),
    align    = c("l", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)
```

### Crowding (2010)

```{r crowding-2010}
Crowding_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    avg_persons_per_room    = weighted.mean(persons_per_room, household_weight, na.rm = TRUE),
    avg_persons_per_bedroom = weighted.mean(persons_per_bedroom, household_weight, na.rm = TRUE),
    overcrowding_rate       = weighted.mean(overcrowded, household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(overcrowding_rate))

Crowding_2010 |>
  mutate(
    avg_persons_per_room    = round(avg_persons_per_room, 2),
    avg_persons_per_bedroom = round(avg_persons_per_bedroom, 2),
    overcrowding_rate       = percent(overcrowding_rate, accuracy = 0.1)
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Household Crowding Indicators by District — 2010 (Weighted)",
    col.names = c("District", "Persons per Room", "Persons per Bedroom", "Overcrowding Rate"),
    align    = c("l", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)
```

::: callout-warning
**Comparability note:** The overcrowding rates in 2010 appear very low (0.0–0.2%) compared to 2022 (6–11%). Before interpreting this as a real increase, verify that bedroom and household size variables are coded consistently across both census waves. The 2010 figure may reflect systematic missing data in the bedroom variable rather than true low crowding. Cross-check raw distributions of `H24_BEDROOMS` in 2010 vs `h2_15` in 2022.
:::

### Spare Bedroom Capacity (2010)

```{r spare-bedrooms-2010}
Spare_bedrooms_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    avg_spare_bedrooms = weighted.mean(spare_bedrooms, household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(avg_spare_bedrooms))

Spare_bedrooms_2010 |>
  mutate(avg_spare_bedrooms = round(avg_spare_bedrooms, 2)) |>
  kbl(
    booktabs = TRUE,
    caption  = "Average Spare Bedroom Capacity by District — 2010 (Weighted)",
    col.names = c("District", "Avg. Spare Bedrooms"),
    align    = c("l", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)
```

### Housing Quality (2010)

```{r housing-quality-2010}
Housing_quality_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    piped_water_rate    = weighted.mean(piped_water, household_weight, na.rm = TRUE),
    electricity_rate    = weighted.mean(electricity, household_weight, na.rm = TRUE),
    improved_toilet_rate = weighted.mean(improved_toilet, household_weight, na.rm = TRUE),
    durable_walls_rate  = weighted.mean(durable_walls, household_weight, na.rm = TRUE),
    durable_roof_rate   = weighted.mean(durable_roof, household_weight, na.rm = TRUE),
    avg_vehicles        = weighted.mean(vehicles_owned, household_weight, na.rm = TRUE),
    .groups = "drop"
  )

Housing_quality_2010 |>
  mutate(
    across(piped_water_rate:durable_roof_rate, ~ percent(., accuracy = 0.1)),
    avg_vehicles = round(avg_vehicles, 2)
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Housing Quality Indicators by District — 2010 (Weighted)",
    col.names = c("District", "Piped Water", "Electricity", "Improved Toilet",
                  "Durable Walls", "Durable Roof", "Avg. Vehicles"),
    align    = c("l", "r", "r", "r", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 10)
```

### Hosting Suitability Index (2010) {#sec-suitability-2010}

A household is classified as hosting-suitable if it has: (1) at least one spare bedroom, (2) piped water, (3) public electricity, and (4) an improved toilet. This index is the **pre-treatment instrument** in the difference-in-differences strategy — it captures structural capacity to host short-term rentals before the platform shock.

$$\text{Suitable}_{i,2010} = \mathbf{1}\left[\text{spare\_bedrooms}_i > 0 \;\cap\; \text{piped\_water}_i \;\cap\; \text{electricity}_i \;\cap\; \text{improved\_toilet}_i\right]$$

$$\text{Suitability}_d = \frac{\sum_{i \in d} w_i \cdot \text{Suitable}_i}{\sum_{i \in d} w_i}$$

```{r suitability-2010}
Suitability_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    suitability_index     = weighted.mean(hosting_suitable, household_weight, na.rm = TRUE),
    suitable_hh_estimated = sum(hosting_suitable * household_weight, na.rm = TRUE),
    total_households      = sum(household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(suitability_index))

Suitability_2010 |>
  mutate(
    suitability_index     = percent(suitability_index, accuracy = 0.1),
    suitable_hh_estimated = comma(round(suitable_hh_estimated)),
    total_households      = comma(round(total_households))
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Hosting Suitability Index by District — 2010 (Pre-Treatment Instrument)",
    col.names = c("District", "Suitability Index", "Suitable HH (Est.)", "Total HH"),
    align    = c("l", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)
```

::: callout-important
**If suitability values are still NA after the fix above**, this indicates the underlying 2010 SPSS variables for water source, toilet type, wall and roof material have a different coding scheme than assumed. Run `count(water_source)`, `count(toilet_type)` etc. on `Thesis_Working_Data_2010` (before the `across()` cleaning) to inspect raw values and adjust thresholds accordingly. The electricity variable (`H21_LIGHTING`) appears to work correctly in the original code, suggesting the other variables may use a different "Not Stated" code.
:::

### 2010 District Summary Table

```{r summary-2010}
District_Summary_2010 <- Rental_supply_2010 |>
  select(district, total_households, rental_share) |>
  left_join(Homeownership_2010 |> select(district, homeownership_rate), by = "district") |>
  left_join(Crowding_2010      |> select(district, overcrowding_rate),  by = "district") |>
  left_join(Suitability_2010   |> select(district, suitability_index),  by = "district") |>
  mutate(census_year = 2010L)

District_Summary_2010 |>
  mutate(
    total_households   = comma(round(total_households)),
    rental_share       = percent(rental_share, accuracy = 0.1),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1),
    overcrowding_rate  = percent(overcrowding_rate, accuracy = 0.1),
    suitability_index  = percent(suitability_index, accuracy = 0.1)
  ) |>
  select(district, total_households, rental_share,
         homeownership_rate, overcrowding_rate, suitability_index) |>
  kbl(
    booktabs = TRUE,
    caption  = "District Housing Indicators — 2010",
    col.names = c("District", "Total HH", "Rental Share",
                  "Ownership Rate", "Overcrowding", "Suitability"),
    align    = c("l", "r", "r", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 10)
```

------------------------------------------------------------------------

# 2022 Census Data

::: callout-note
**Note on STR variable:** The `dwell_status` variable (Short-Term Occupation = 8, AirBNB = 12) has been requested from the Statistics Office and will be incorporated once received. The analysis currently uses long-term rental and homeownership indicators as proxies.
:::

## Loading 2022 Data

```{r load-2022}
Raw_Census_Data_2022 <- read_sav("PersonHHoldMerge 2022 Annon.sav")
```

## 2022 Column Labels

```{r labels-2022}
labels_table_2022 <- tibble(
  variable_name       = names(Raw_Census_Data_2022),
  SPSS_variable_label = sapply(Raw_Census_Data_2022, function(x) {
    lab <- labelled::var_label(x)
    if (is.null(lab) || lab == "") NA_character_ else as.character(lab)
  }),
  SPSS_value_labels   = sapply(Raw_Census_Data_2022, function(x) {
    vals <- labelled::val_labels(x)
    if (length(vals) == 0) NA_character_
    else paste(names(vals), vals, collapse = "; ")
  })
)

print(labels_table_2022, n = Inf, width = Inf)
```

## Creating 2022 Working Table

```{r working-table-2022}
Thesis_Working_Data_2022 <- Raw_Census_Data_2022 |>
  distinct(CompositeKey, .keep_all = TRUE) |>
  select(
    CompositeKey,
    DISTRICT_ID, CONSTITUENCY,
    num_males, num_females, Npersons,
    h2_1, h2_3a, h2_3b1, h2_3b2,
    h2_5, h2_6, h2_7, h2_8,
    h2_11a, h2_12, h2_14, h2_15, h2_21,
    HHLD_WEIGHT
  ) |>
  rename(
    household_id    = CompositeKey,
    district        = DISTRICT_ID,
    constituency    = CONSTITUENCY,
    males           = num_males,
    females         = num_females,
    household_size  = Npersons,
    building_type   = h2_1,
    tenure_status   = h2_3a,
    monthly_rent    = h2_3b1,
    rent_furnishing = h2_3b2,
    roof_material   = h2_5,
    wall_material   = h2_6,
    year_built      = h2_7,
    water_source    = h2_8,
    toilet_type     = h2_11a,
    lighting_source = h2_12,
    rooms           = h2_14,
    bedrooms        = h2_15,
    vehicles_owned  = h2_21,
    household_weight = HHLD_WEIGHT
  ) |>
  zap_labels() |>
  mutate(
    district = case_when(
      district == 1  ~ "Castries 1",
      district == 2  ~ "Castries 2",
      district == 3  ~ "Castries 3",
      district == 4  ~ "Anse La Raye",
      district == 5  ~ "Canaries",
      district == 6  ~ "Soufriere",
      district == 7  ~ "Choiseul",
      district == 8  ~ "Laborie",
      district == 9  ~ "Vieux Fort",
      district == 10 ~ "Micoud",
      district == 11 ~ "Dennery",
      district == 12 ~ "Gros Islet",
      is.na(district) ~ NA_character_,
      TRUE            ~ paste0("Unknown (", district, ")")
    ),
    monthly_rent = as.numeric(monthly_rent),
    across(
      c(males, females, household_size, monthly_rent, rooms, bedrooms,
        vehicles_owned, roof_material, wall_material, year_built,
        water_source, toilet_type, lighting_source, tenure_status,
        building_type),
      ~ if_else(. %in% c(-999999999, 999999999), NA_real_, as.numeric(.))
    )
  ) |>
  filter(!is.na(district))
```

::: callout-warning
**Missing districts in 2022:** Several large districts (Castries 2, Castries 3, Gros Islet, Micoud, Dennery, Choiseul) return NA for crowding and suitability indicators. This warrants investigation — run `count(rooms)` and `count(bedrooms)` on these districts' subset to determine whether the bedroom/rooms variables are genuinely missing or encoded differently (e.g., using a different sentinel value such as `-999999999` for zero rooms rather than actual zero). If the issue is a zero-rooms coding problem, replace `if_else(rooms > 0, rooms, NA_real_)` with `if_else(!is.na(rooms) & rooms > 0, rooms, NA_real_)` after verifying the raw distributions.
:::

## 2022 Working Data Labels

```{r data-labels-2022}
working_data_labels_2022 <- tibble(
  variable    = names(Thesis_Working_Data_2022),
  variable_label = sapply(Thesis_Working_Data_2022, function(x) {
    lab <- attr(x, "label")
    if (is.null(lab)) NA_character_ else as.character(lab)
  }),
  value_labels = sapply(Thesis_Working_Data_2022, function(x) {
    vals <- attr(x, "labels")
    if (is.null(vals)) NA_character_
    else paste(names(vals), vals, collapse = "; ")
  })
)

print(working_data_labels_2022, n = Inf, width = Inf)
```

## 2022 Variable Reference Table

```{r var-ref-2022}
tibble(
  Variable    = names(Thesis_Working_Data_2022),
  Description = c(
    "Household unique identifier", "Administrative district",
    "Electoral constituency", "Number of male household members",
    "Number of female household members", "Total persons in household",
    "Type of building structure", "Housing tenure status",
    "Monthly rent paid", "Rental furnishing status", "Roof material",
    "Wall material", "Year dwelling constructed", "Main water source",
    "Type of toilet facility", "Main lighting source",
    "Total number of rooms", "Number of bedrooms",
    "Number of vehicles owned", "Survey household weight"
  )
) |>
  kbl(booktabs = TRUE, caption = "Working Dataset Variable Reference — 2022") |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 10) |>
  column_spec(1, bold = TRUE, width = "3.5cm") |>
  column_spec(2, width = "10cm")
```

## Derive 2022 Indicators

```{r indicators-2022}
Thesis_Working_Data_2022 <- Thesis_Working_Data_2022 |>
  mutate(
    # Tenure
    long_term_rental = if_else(tenure_status %in% c(7, 8, 10), 1, 0),
    owner_occupied   = if_else(tenure_status %in% c(1, 2, 3, 4), 1, 0),
    # Housing quality
    piped_water      = if_else(water_source %in% c(1, 2), 1, 0),
    electricity      = if_else(lighting_source == 1, 1, 0),
    improved_toilet  = if_else(toilet_type %in% c(1, 2, 3), 1, 0),
    durable_walls    = if_else(wall_material %in% c(1, 2, 3), 1, 0),
    durable_roof     = if_else(roof_material %in% c(1, 2, 3), 1, 0),
    # Crowding
    rooms_clean          = if_else(rooms > 0, rooms, NA_real_),
    bedrooms_clean       = if_else(bedrooms > 0, bedrooms, NA_real_),
    persons_per_room     = household_size / rooms_clean,
    persons_per_bedroom  = household_size / bedrooms_clean,
    overcrowded          = if_else(persons_per_bedroom > 2, 1, 0),
    spare_bedrooms       = bedrooms_clean - household_size,
    # Hosting suitability
    hosting_suitable = if_else(
      spare_bedrooms > 0 &
      piped_water    == 1 &
      electricity    == 1 &
      improved_toilet == 1,
      1, 0
    ),
    census_year = 2022L
  )
```

## Short-Term Rentals Per District (2022) {#sec-str-var}

The `dwell_status` variable (Short-Term Occupation = 8, AirBNB = 12) has been requested from the Statistics Office and will be incorporated once received. When available:

$$\text{STR}_i = \begin{cases} 1 & \text{if } \mathtt{dwell\_status}_i \in \{8, 12\} \\ 0 & \text{otherwise} \end{cases}$$

$$\text{STR}_d = \sum_{i \in d} \text{STR}_i \times w_i$$

## Rental Supply by District (2022)

```{r rental-supply-2022}
Rental_supply_2022 <- Thesis_Working_Data_2022 |>
  group_by(district) |>
  summarise(
    long_term_rentals = sum(long_term_rental * household_weight, na.rm = TRUE),
    total_households  = sum(household_weight, na.rm = TRUE),
    rental_share      = long_term_rentals / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(long_term_rentals))

Rental_supply_2022 |>
  mutate(
    long_term_rentals = comma(round(long_term_rentals)),
    total_households  = comma(round(total_households)),
    rental_share      = percent(rental_share, accuracy = 0.1)
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Long-Term Rental Supply by District — 2022 (Weighted)",
    col.names = c("District", "Long-Term Rentals", "Total Households", "Rental Share"),
    align    = c("l", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)

Rental_supply_2022 |>
  filter(!is.na(district)) |>
  ggplot(aes(x = reorder(district, rental_share), y = rental_share)) +
  geom_col(fill = "#2C7BB6") +
  geom_text(aes(label = percent(rental_share, accuracy = 0.1)),
            hjust = -0.1, size = 2.8) +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  labs(title = "Long-Term Rental Share by District — 2022",
       x = NULL, y = "Share of Total Households", caption = caption_2022)
```

## Average Monthly Rent by District (2022)

```{r avg-rent-2022}
Rent_per_district_2022 <- Thesis_Working_Data_2022 |>
  filter(tenure_status %in% c(7, 8, 10),
         !is.na(monthly_rent), monthly_rent > 0, monthly_rent < 99999) |>
  group_by(district) |>
  summarise(
    avg_monthly_rent    = weighted.mean(monthly_rent, household_weight, na.rm = TRUE),
    renting_households  = sum(household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  complete(district = unique(
    Thesis_Working_Data_2022$district[!is.na(Thesis_Working_Data_2022$district)]
  )) |>
  arrange(desc(avg_monthly_rent))

Rent_per_district_2022 |>
  mutate(
    avg_monthly_rent   = dollar(round(avg_monthly_rent), prefix = "EC$"),
    renting_households = comma(round(renting_households))
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Average Monthly Long-Term Rent by District — 2022 (Weighted)",
    col.names = c("District", "Avg. Monthly Rent", "Renting Households"),
    align    = c("l", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)

Rent_per_district_2022 |>
  ggplot(aes(x = avg_monthly_rent, y = reorder(district, avg_monthly_rent))) +
  geom_segment(aes(x = 0, xend = avg_monthly_rent, y = district, yend = district),
               color = "grey75", linewidth = 0.6) +
  geom_point(size = 3, color = "#2C7BB6") +
  geom_text(aes(label = dollar(round(avg_monthly_rent), prefix = "EC$")),
            hjust = -0.15, size = 2.8) +
  scale_x_continuous(labels = dollar_format(prefix = "EC$"),
                     expand = expansion(mult = c(0, 0.18))) +
  labs(title = "Average Monthly Long-Term Rent by District — 2022",
       x = NULL, y = NULL, caption = caption_2022)
```

## Home Ownership Rates by District (2022)

```{r homeownership-2022}
Homeownership_2022 <- Thesis_Working_Data_2022 |>
  group_by(district) |>
  summarise(
    owner_households   = sum(owner_occupied * household_weight, na.rm = TRUE),
    total_households   = sum(household_weight, na.rm = TRUE),
    homeownership_rate = owner_households / total_households,
    .groups = "drop"
  ) |>
  arrange(desc(homeownership_rate))

Homeownership_2022 |>
  mutate(
    owner_households   = comma(round(owner_households)),
    total_households   = comma(round(total_households)),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1)
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Home Ownership Rates by District — 2022 (Weighted)",
    col.names = c("District", "Owner Households", "Total Households", "Ownership Rate"),
    align    = c("l", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)

Homeownership_2022 |>
  left_join(Rental_supply_2022 |> select(district, rental_share), by = "district") |>
  select(district, homeownership_rate, rental_share) |>
  pivot_longer(cols = c(homeownership_rate, rental_share),
               names_to = "metric", values_to = "value") |>
  mutate(metric = recode(metric,
    "homeownership_rate" = "Homeownership Rate",
    "rental_share"       = "Long-Term Rental Share")) |>
  ggplot(aes(x = reorder(district, value), y = value, fill = metric)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(values = c("#2C7BB6", "#D7191C")) +
  coord_flip() +
  labs(title = "Homeownership Rate vs Long-Term Rental Share — 2022",
       x = NULL, y = NULL, fill = NULL, caption = caption_2022)
```

## Household Crowding Indicators (2022)

```{r crowding-2022}
Crowding_2022 <- Thesis_Working_Data_2022 |>
  group_by(district) |>
  summarise(
    avg_persons_per_room    = weighted.mean(persons_per_room, household_weight, na.rm = TRUE),
    avg_persons_per_bedroom = weighted.mean(persons_per_bedroom, household_weight, na.rm = TRUE),
    overcrowding_rate       = weighted.mean(overcrowded, household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(overcrowding_rate))

Crowding_2022 |>
  mutate(
    avg_persons_per_room    = round(avg_persons_per_room, 2),
    avg_persons_per_bedroom = round(avg_persons_per_bedroom, 2),
    overcrowding_rate       = percent(overcrowding_rate, accuracy = 0.1)
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Household Crowding Indicators by District — 2022 (Weighted)",
    col.names = c("District", "Persons per Room", "Persons per Bedroom", "Overcrowding Rate"),
    align    = c("l", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)

Crowding_2022 |>
  filter(!is.na(overcrowding_rate)) |>
  ggplot(aes(x = reorder(district, overcrowding_rate), y = overcrowding_rate)) +
  geom_col(fill = "#D7191C") +
  geom_text(aes(label = percent(overcrowding_rate, accuracy = 0.1)),
            hjust = -0.1, size = 2.8) +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.15))) +
  coord_flip() +
  labs(title = "Overcrowding Rate by District — 2022",
       subtitle = "Share of households with more than 2 persons per bedroom",
       x = NULL, y = "Overcrowding Rate", caption = caption_2022)
```

## Spare Bedroom Capacity (2022)

```{r spare-bedrooms-2022}
Spare_bedrooms_2022 <- Thesis_Working_Data_2022 |>
  group_by(district) |>
  summarise(
    avg_spare_bedrooms = weighted.mean(spare_bedrooms, household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(avg_spare_bedrooms))

Spare_bedrooms_2022 |>
  filter(!is.na(avg_spare_bedrooms)) |>
  mutate(avg_spare_bedrooms = round(avg_spare_bedrooms, 2)) |>
  kbl(
    booktabs = TRUE,
    caption  = "Average Spare Bedroom Capacity by District — 2022 (Weighted)",
    col.names = c("District", "Avg. Spare Bedrooms"),
    align    = c("l", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)
```

## Housing Quality Indicators (2022)

```{r housing-quality-2022}
Housing_quality_2022 <- Thesis_Working_Data_2022 |>
  group_by(district) |>
  summarise(
    piped_water_rate     = weighted.mean(piped_water, household_weight, na.rm = TRUE),
    electricity_rate     = weighted.mean(electricity, household_weight, na.rm = TRUE),
    improved_toilet_rate = weighted.mean(improved_toilet, household_weight, na.rm = TRUE),
    durable_walls_rate   = weighted.mean(durable_walls, household_weight, na.rm = TRUE),
    durable_roof_rate    = weighted.mean(durable_roof, household_weight, na.rm = TRUE),
    avg_vehicles         = weighted.mean(vehicles_owned, household_weight, na.rm = TRUE),
    .groups = "drop"
  )

Housing_quality_2022 |>
  filter(!is.na(piped_water_rate)) |>
  mutate(
    across(piped_water_rate:durable_roof_rate, ~ percent(., accuracy = 0.1)),
    avg_vehicles = round(avg_vehicles, 2)
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Housing Quality Indicators by District — 2022 (Weighted)",
    col.names = c("District", "Piped Water", "Electricity", "Improved Toilet",
                  "Durable Walls", "Durable Roof", "Avg. Vehicles"),
    align    = c("l", "r", "r", "r", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 10)
```

## Housing Age by District (2022)

```{r housing-age-2022}
Year_built_2022 <- Thesis_Working_Data_2022 |>
  filter(!is.na(year_built)) |>
  group_by(district) |>
  summarise(
    avg_year_built_index = weighted.mean(year_built, household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(avg_year_built_index))

Year_built_2022 |>
  filter(!is.na(avg_year_built_index)) |>
  mutate(avg_year_built_index = round(avg_year_built_index, 2)) |>
  kbl(
    booktabs = TRUE,
    caption  = "Average Housing Age Index by District — 2022 (1=Before 1980, higher=more recent)",
    col.names = c("District", "Avg. Year Built Index"),
    align    = c("l", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)
```

## Hosting Suitability Index (2022)

```{r suitability-2022}
Suitability_2022 <- Thesis_Working_Data_2022 |>
  group_by(district) |>
  summarise(
    suitability_index     = weighted.mean(hosting_suitable, household_weight, na.rm = TRUE),
    suitable_hh_estimated = sum(hosting_suitable * household_weight, na.rm = TRUE),
    total_households      = sum(household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(suitability_index))

Suitability_2022 |>
  mutate(
    suitability_index     = percent(suitability_index, accuracy = 0.1),
    suitable_hh_estimated = comma(round(suitable_hh_estimated)),
    total_households      = comma(round(total_households))
  ) |>
  kbl(
    booktabs = TRUE,
    caption  = "Hosting Suitability Index by District — 2022",
    col.names = c("District", "Suitability Index", "Suitable HH (Est.)", "Total HH"),
    align    = c("l", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11)

Suitability_2022 |>
  filter(!is.na(suitability_index)) |>
  ggplot(aes(x = reorder(district, suitability_index), y = suitability_index,
             fill = suitability_index)) +
  geom_col() +
  geom_text(aes(label = percent(suitability_index, accuracy = 0.1)),
            hjust = -0.1, size = 2.8) +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.15))) +
  scale_fill_gradient(low = "#fee8c8", high = "#e34a33", guide = "none") +
  coord_flip() +
  labs(title = "Hosting Suitability Index by District — 2022",
       subtitle = "Share of households with spare bedroom, piped water, electricity & improved toilet",
       x = NULL, y = "Suitability Index", caption = caption_2022)
```

## 2022 District Summary Table

```{r summary-2022}
District_Summary_2022 <- Rental_supply_2022 |>
  select(district, long_term_rentals, total_households, rental_share) |>
  left_join(Rent_per_district_2022  |> select(district, avg_monthly_rent, renting_households),   by = "district") |>
  left_join(Homeownership_2022      |> select(district, owner_households, homeownership_rate),   by = "district") |>
  left_join(Crowding_2022           |> select(district, avg_persons_per_room,
                                               avg_persons_per_bedroom, overcrowding_rate),       by = "district") |>
  left_join(Spare_bedrooms_2022     |> select(district, avg_spare_bedrooms),                     by = "district") |>
  left_join(Housing_quality_2022    |> select(district, piped_water_rate, electricity_rate,
                                               improved_toilet_rate, durable_walls_rate,
                                               durable_roof_rate, avg_vehicles),                 by = "district") |>
  left_join(Year_built_2022         |> select(district, avg_year_built_index),                   by = "district") |>
  left_join(Suitability_2022        |> select(district, suitability_index),                      by = "district") |>
  arrange(desc(total_households))

District_Summary_2022 |>
  mutate(
    total_households   = comma(round(total_households)),
    rental_share       = percent(rental_share, accuracy = 0.1),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1),
    overcrowding_rate  = percent(overcrowding_rate, accuracy = 0.1),
    suitability_index  = percent(suitability_index, accuracy = 0.1),
    avg_monthly_rent   = dollar(round(avg_monthly_rent), prefix = "EC$"),
    avg_persons_per_room   = round(avg_persons_per_room, 2),
    avg_spare_bedrooms     = round(avg_spare_bedrooms, 2)
  ) |>
  select(district, total_households, rental_share, homeownership_rate,
         avg_monthly_rent, overcrowding_rate, suitability_index) |>
  kbl(
    booktabs = TRUE,
    caption  = "District Summary: Key Housing Indicators — 2022",
    col.names = c("District", "Total HH", "Rental Share", "Ownership Rate",
                  "Avg. Rent", "Overcrowding", "Suitability"),
    align    = c("l", "r", "r", "r", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 10) |>
  add_header_above(c(" " = 2, "Tenure" = 2, "Affordability" = 1,
                     "Crowding" = 1, "STR Potential" = 1))

# Scatter: overcrowding vs rental share (displacement pattern)
District_Summary_2022 |>
  filter(!is.na(overcrowding_rate), !is.na(rental_share)) |>
  ggplot(aes(x = rental_share, y = overcrowding_rate, label = district)) +
  geom_point(aes(size = total_households), color = "#2C7BB6", alpha = 0.7) +
  geom_text_repel(size = 2.8, max.overlaps = 12) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  scale_size_continuous(labels = comma, range = c(2, 8),
                        guide  = guide_legend(title = "Total Households")) +
  labs(title    = "Overcrowding Rate vs Long-Term Rental Share — 2022",
       subtitle  = "Larger points indicate more households. Suggests displacement pattern.",
       x = "Long-Term Rental Share", y = "Overcrowding Rate", caption = caption_2022)
```

------------------------------------------------------------------------

# Difference-in-Differences Panel

## Building the Panel Dataset

```{r build-panel}
Panel_2010 <- Rental_supply_2010 |>
  select(district, total_households, rental_share) |>
  left_join(Homeownership_2010 |> select(district, homeownership_rate), by = "district") |>
  left_join(Crowding_2010      |> select(district, overcrowding_rate),  by = "district") |>
  left_join(Suitability_2010   |> select(district, suitability_index),  by = "district") |>
  mutate(census_year = 2010L)

Panel_2022 <- Rental_supply_2022 |>
  select(district, total_households, rental_share) |>
  left_join(Homeownership_2022 |> select(district, homeownership_rate), by = "district") |>
  left_join(Crowding_2022      |> select(district, overcrowding_rate),  by = "district") |>
  left_join(Suitability_2022   |> select(district, suitability_index),  by = "district") |>
  mutate(census_year = 2022L)

# Stack into balanced panel
# The treatment intensity is the 2010 suitability index, held fixed at pre-treatment value
District_Panel <- bind_rows(Panel_2010, Panel_2022) |>
  arrange(district, census_year) |>
  # Merge in the 2010 suitability index as treatment intensity (time-invariant)
  left_join(
    Panel_2010 |> select(district, suitability_2010 = suitability_index),
    by = "district"
  ) |>
  mutate(post = if_else(census_year == 2022L, 1L, 0L))

District_Panel |>
  mutate(
    total_households   = comma(round(total_households)),
    rental_share       = percent(rental_share, accuracy = 0.1),
    homeownership_rate = percent(homeownership_rate, accuracy = 0.1),
    overcrowding_rate  = percent(overcrowding_rate, accuracy = 0.1),
    suitability_2010   = percent(suitability_2010, accuracy = 0.1)
  ) |>
  select(district, census_year, total_households, rental_share,
         homeownership_rate, overcrowding_rate, suitability_2010) |>
  kbl(
    booktabs = TRUE,
    caption  = "District Housing Indicators: 2010 vs 2022",
    col.names = c("District", "Year", "Total HH", "Rental Share",
                  "Ownership Rate", "Overcrowding", "2010 Suitability"),
    align    = c("l", "c", "r", "r", "r", "r", "r")
  ) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 10) |>
  collapse_rows(columns = 1, valign = "middle")
```

## Panel Change Visualisations

```{r panel-viz}
District_Panel |>
  filter(!is.na(rental_share)) |>
  ggplot(aes(x = factor(census_year), y = rental_share,
             group = district, color = district)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  scale_y_continuous(labels = percent) +
  labs(title    = "Long-Term Rental Share by District: 2010 vs 2022",
       subtitle  = "Lines connect the same district across census years",
       x = "Census Year", y = "Rental Share", color = "District",
       caption = caption_both)

District_Panel |>
  filter(!is.na(homeownership_rate)) |>
  ggplot(aes(x = factor(census_year), y = homeownership_rate,
             group = district, color = district)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  scale_y_continuous(labels = percent) +
  labs(title    = "Homeownership Rate by District: 2010 vs 2022",
       subtitle  = "Lines connect the same district across census years",
       x = "Census Year", y = "Homeownership Rate", color = "District",
       caption = caption_both)
```

------------------------------------------------------------------------

# Suitability Index Diagnostic {#sec-diagnostic-suitability}

Before running regressions, we must verify whether the 2010 suitability index is computing correctly. The block below inspects the raw 2010 variable distributions, automatically detects the correct "Not Stated" codes, and recomputes the suitability index with the corrected cleaning.

```{r fix-suitability}
# ── Step 1: Inspect raw distributions to find actual NA codes ──────────────
cat("=== 2010 H18_WATER (water source) raw value counts ===\n")
water_raw <- Raw_Census_Data_2010 |>
  filter(!is.na(H18_WATER)) |>
  count(H18_WATER) |>
  arrange(H18_WATER)
print(water_raw, n = 30)

cat("\n=== 2010 H20_TOILET (toilet type) raw value counts ===\n")
toilet_raw <- Raw_Census_Data_2010 |>
  filter(!is.na(H20_TOILET)) |>
  count(H20_TOILET) |>
  arrange(H20_TOILET)
print(toilet_raw, n = 30)

cat("\n=== 2010 H15_WALLS (wall material) raw value counts ===\n")
wall_raw <- Raw_Census_Data_2010 |>
  filter(!is.na(H15_WALLS)) |>
  count(H15_WALLS) |>
  arrange(H15_WALLS)
print(wall_raw, n = 30)

cat("\n=== 2010 H16_ROOF (roof material) raw value counts ===\n")
roof_raw <- Raw_Census_Data_2010 |>
  filter(!is.na(H16_ROOF)) |>
  count(H16_ROOF) |>
  arrange(H16_ROOF)
print(roof_raw, n = 30)

cat("\n=== 2010 H21_LIGHTING (lighting source) raw value counts ===\n")
lighting_raw <- Raw_Census_Data_2010 |>
  filter(!is.na(H21_LIGHTING)) |>
  count(H21_LIGHTING) |>
  arrange(H21_LIGHTING)
print(lighting_raw, n = 20)

cat("\n=== 2010 H24_BEDROOMS raw value counts ===\n")
bed_raw <- Raw_Census_Data_2010 |>
  filter(!is.na(H24_BEDROOMS)) |>
  count(H24_BEDROOMS) |>
  arrange(H24_BEDROOMS)
print(bed_raw, n = 20)
```

```{r fix-suitability-2}
# ── Step 2: Infer sentinel values from the distributions above ──────────────
# Logic: values above a plausible maximum (e.g. water codes 1-8 → 9 is NS;
# bedroom codes 0-10 → 99 is NS; etc.) are treated as missing.
# We detect the "gap" automatically: anything > the 99th percentile of
# labelled values AND not a round number in the expected coding range.

# Helper: given a numeric vector, return all values that look like sentinels
# (i.e. they are large outliers inconsistent with the expected code range)
detect_sentinels <- function(x) {
  x_num <- as.numeric(x)
  x_valid <- x_num[!is.na(x_num)]
  if (length(x_valid) == 0) return(numeric(0))
  # Sentinels are values > 3× the 95th percentile of the non-extreme values
  q95 <- quantile(x_valid[x_valid < 1e6], 0.95, na.rm = TRUE)
  sentinels <- unique(x_valid[x_valid > max(3 * q95, 20)])
  sentinels
}

# Apply to each quality variable and report what will be treated as NA
vars_to_check <- c("H18_WATER", "H20_TOILET", "H15_WALLS",
                   "H16_ROOF", "H21_LIGHTING", "H24_BEDROOMS", "H23_ROOMS")

sentinel_report <- map_dfr(vars_to_check, function(v) {
  vals <- as.numeric(Raw_Census_Data_2010[[v]])
  sents <- detect_sentinels(vals)
  tibble(variable = v, sentinel_values = paste(sents, collapse = ", "),
         n_affected = sum(vals %in% sents, na.rm = TRUE))
})

cat("\n=== Auto-detected sentinel values per variable ===\n")
print(sentinel_report)

# ── Step 3: Recompute working table with auto-detected sentinels ─────────────
# Get all sentinel values across the quality variables
all_sentinels <- map(vars_to_check, function(v) {
  detect_sentinels(as.numeric(Raw_Census_Data_2010[[v]]))
}) |> unlist() |> unique()

# Also always include the canonical large sentinel
all_sentinels <- unique(c(all_sentinels, -999999999, 999999999))

cat("\nAll values that will be treated as NA:", paste(all_sentinels, collapse = ", "), "\n")

# Recompute Thesis_Working_Data_2010 with corrected cleaning
Thesis_Working_Data_2010 <- Thesis_Working_Data_2010 |>
  mutate(
    # Re-clean quality variables using all detected sentinels
    water_source_c  = if_else(water_source  %in% all_sentinels, NA_real_, water_source),
    toilet_type_c   = if_else(toilet_type   %in% all_sentinels, NA_real_, toilet_type),
    wall_material_c = if_else(wall_material %in% all_sentinels, NA_real_, wall_material),
    roof_material_c = if_else(roof_material %in% all_sentinels, NA_real_, roof_material),
    lighting_c      = if_else(lighting_source %in% all_sentinels, NA_real_, lighting_source),
    bedrooms_c2     = if_else(bedrooms %in% all_sentinels | bedrooms <= 0, NA_real_, bedrooms),
    rooms_c2        = if_else(rooms    %in% all_sentinels | rooms    <= 0, NA_real_, rooms),
    # Recompute quality flags
    piped_water     = if_else(water_source_c  %in% c(1, 2), 1, 0),
    electricity     = if_else(lighting_c      == 1,         1, 0),
    improved_toilet = if_else(toilet_type_c   %in% c(1, 2, 3), 1, 0),
    durable_walls   = if_else(wall_material_c %in% c(1, 2, 3), 1, 0),
    durable_roof    = if_else(roof_material_c %in% c(1, 2, 3), 1, 0),
    # Recompute crowding
    persons_per_bedroom = household_size / bedrooms_c2,
    overcrowded         = if_else(persons_per_bedroom > 2, 1, 0),
    spare_bedrooms      = bedrooms_c2 - household_size,
    # Recompute suitability
    hosting_suitable = if_else(
      !is.na(spare_bedrooms)  & spare_bedrooms  > 0 &
      !is.na(piped_water)     & piped_water      == 1 &
      !is.na(electricity)     & electricity      == 1 &
      !is.na(improved_toilet) & improved_toilet  == 1,
      1, 0
    )
  )

cat("\n=== Hosting suitability flag distribution after fix ===\n")
Thesis_Working_Data_2010 |>
  count(hosting_suitable) |>
  print()

cat("\n=== piped_water flag distribution ===\n")
Thesis_Working_Data_2010 |> count(piped_water) |> print()

cat("\n=== electricity flag distribution ===\n")
Thesis_Working_Data_2010 |> count(electricity) |> print()

cat("\n=== improved_toilet flag distribution ===\n")
Thesis_Working_Data_2010 |> count(improved_toilet) |> print()
```

```{r recompute-suitability-2010}
# ── Step 4: Recompute district-level suitability with corrected data ──────────
Suitability_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    suitability_index     = weighted.mean(hosting_suitable, household_weight, na.rm = TRUE),
    suitable_hh_estimated = sum(hosting_suitable * household_weight, na.rm = TRUE),
    total_households      = sum(household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(suitability_index))

cat("\n=== Corrected 2010 Suitability Index ===\n")
print(Suitability_2010)

# Also recompute crowding with corrected bedrooms
Crowding_2010 <- Thesis_Working_Data_2010 |>
  group_by(district) |>
  summarise(
    avg_persons_per_room    = weighted.mean(household_size / rooms_c2,   household_weight, na.rm = TRUE),
    avg_persons_per_bedroom = weighted.mean(persons_per_bedroom,          household_weight, na.rm = TRUE),
    overcrowding_rate       = weighted.mean(overcrowded,                  household_weight, na.rm = TRUE),
    .groups = "drop"
  ) |>
  arrange(desc(overcrowding_rate))

cat("\n=== Corrected 2010 Crowding ===\n")
print(Crowding_2010)
```

```{r rebuild-panel}
# ── Step 5: Rebuild the panel with corrected suitability ──────────────────────
Panel_2010 <- Rental_supply_2010 |>
  select(district, total_households, rental_share) |>
  left_join(Homeownership_2010 |> select(district, homeownership_rate), by = "district") |>
  left_join(Crowding_2010      |> select(district, overcrowding_rate),  by = "district") |>
  left_join(Suitability_2010   |> select(district, suitability_index),  by = "district") |>
  mutate(census_year = 2010L)

District_Panel <- bind_rows(Panel_2010, Panel_2022) |>
  arrange(district, census_year) |>
  left_join(
    Panel_2010 |> select(district, suitability_2010 = suitability_index),
    by = "district"
  ) |>
  mutate(post = if_else(census_year == 2022L, 1L, 0L))

cat("\n=== Panel suitability_2010 coverage ===\n")
District_Panel |>
  distinct(district, suitability_2010) |>
  mutate(has_suitability = !is.na(suitability_2010)) |>
  count(has_suitability) |>
  print()
```

------------------------------------------------------------------------

# Regression Analysis {#sec-regression}

The treatment variable is the 2010 Hosting Suitability Index from @sec-diagnostic-suitability. The regressions use a **conditional approach**: if the suitability index is available for enough districts (≥ 4), the full DiD with district + year fixed effects is run. If suitability remains partially or fully missing, the analysis falls back to the **first-differences estimator** — regressing the 2010→2022 change in each outcome on the change in the 2010 suitability index — which only requires that the *outcome variables* are observed (which they are).

The estimating equation for the DiD specification is:

$$Y_{dt} = \alpha_d + \gamma_t + \beta (\text{Suitability}_{d,2010} \times \text{Post}_t) + \varepsilon_{dt}$$

## Check Suitability Availability and Route to Estimator

```{r check-and-route}
n_valid_suitability <- District_Panel |>
  filter(!is.na(suitability_2010)) |>
  distinct(district) |>
  nrow()

cat("Districts with valid 2010 suitability:", n_valid_suitability, "of 12\n")

use_did <- n_valid_suitability >= 4
cat("Estimation route:", if (use_did) "Full DiD (feols)" else "First-differences OLS fallback", "\n")
```

## First-Differences Analysis (Always Runs)

This estimator requires no assumptions about the suitability index. It regresses the district-level *change* in each outcome (2022 − 2010) on the 2010 suitability index, using only districts where both years are observed.

```{r first-diff}
# Compute first differences — this works regardless of suitability NA status
# Pull 2022 household counts separately for weights (avoids pivot_wider naming issues)
weights_2022 <- District_Panel |>
  filter(census_year == 2022) |>
  select(district, total_households_2022 = total_households)

First_diff <- District_Panel |>
  select(district, census_year, rental_share, homeownership_rate,
         overcrowding_rate, suitability_2010) |>
  pivot_wider(
    names_from  = census_year,
    values_from = c(rental_share, homeownership_rate, overcrowding_rate)
  ) |>
  left_join(weights_2022, by = "district") |>
  mutate(
    d_rental_share       = rental_share_2022       - rental_share_2010,
    d_homeownership_rate = homeownership_rate_2022  - homeownership_rate_2010,
    d_overcrowding_rate  = overcrowding_rate_2022   - overcrowding_rate_2010
  )

cat("=== First-differences dataset ===\n")
First_diff |>
  select(district, suitability_2010, total_households_2022,
         d_rental_share, d_homeownership_rate, d_overcrowding_rate) |>
  mutate(across(where(is.numeric), ~ round(., 4))) |>
  print()

# OLS on changes — works even when suitability is all NA (intercept-only in that case)
fd_rental <- lm(d_rental_share       ~ suitability_2010,
                data    = First_diff |> filter(!is.na(d_rental_share) & !is.na(total_households_2022)),
                weights = total_households_2022)
fd_own    <- lm(d_homeownership_rate ~ suitability_2010,
                data    = First_diff |> filter(!is.na(d_homeownership_rate) & !is.na(total_households_2022)),
                weights = total_households_2022)
fd_crowd  <- lm(d_overcrowding_rate  ~ suitability_2010,
                data    = First_diff |> filter(!is.na(d_overcrowding_rate) & !is.na(total_households_2022)),
                weights = total_households_2022)

modelsummary(
  list(
    "Δ Rental Share"       = fd_rental,
    "Δ Homeownership Rate" = fd_own,
    "Δ Overcrowding Rate"  = fd_crowd
  ),
  coef_rename = c(
    "(Intercept)"      = "Intercept",
    "suitability_2010" = "2010 Suitability Index"
  ),
  stars   = c("*" = 0.10, "**" = 0.05, "***" = 0.01),
  gof_map = c("nobs", "r.squared", "adj.r.squared"),
  title   = "First-Differences: Change in Housing Outcomes (2022−2010) on 2010 Suitability",
  notes   = c(
    "Dependent variable is the district-level change from 2010 to 2022.",
    "Weighted by 2022 district household count.",
    "If suitability_2010 is all NA, only the intercept (mean change) is identified.",
    "* p<0.10, ** p<0.05, *** p<0.01"
  )
)
```

## Full DiD (Runs If Suitability Available for ≥ 4 Districts)

```{r did-main}
if (use_did) {

  model_rental <- feols(
    rental_share ~ suitability_2010:post | district + census_year,
    data    = District_Panel |> filter(!is.na(suitability_2010)),
    weights = ~ total_households
  )

  model_own <- feols(
    homeownership_rate ~ suitability_2010:post | district + census_year,
    data    = District_Panel |> filter(!is.na(suitability_2010)),
    weights = ~ total_households
  )

  model_crowd <- feols(
    overcrowding_rate ~ suitability_2010:post | district + census_year,
    data    = District_Panel |>
                filter(!is.na(suitability_2010) & !is.na(overcrowding_rate)),
    weights = ~ total_households
  )

  modelsummary(
    list(
      "Rental Share"       = model_rental,
      "Homeownership Rate" = model_own,
      "Overcrowding Rate"  = model_crowd
    ),
    coef_rename = c("suitability_2010:post" = "Suitability (2010) × Post"),
    stars   = c("*" = 0.10, "**" = 0.05, "***" = 0.01),
    gof_map = c("nobs", "r.squared", "FE: district", "FE: census_year"),
    title   = "DiD Estimates: Effect of 2010 Hosting Suitability on Housing Outcomes (2010–2022)",
    notes   = c(
      "District and year fixed effects in all specifications.",
      "Weighted by district total households.",
      "N ≤ 24 (12 districts × 2 years). Results suggestive given small N.",
      "* p<0.10, ** p<0.05, *** p<0.01"
    )
  )

  # Coefficient plot
  bind_rows(
    tidy(model_rental, conf.int = TRUE) |> mutate(outcome = "Rental Share"),
    tidy(model_own,    conf.int = TRUE) |> mutate(outcome = "Homeownership Rate"),
    tidy(model_crowd,  conf.int = TRUE) |> mutate(outcome = "Overcrowding Rate")
  ) |>
    filter(str_detect(term, "suitability")) |>
    ggplot(aes(x = outcome, y = estimate, ymin = conf.low, ymax = conf.high)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
    geom_pointrange(color = "#2C7BB6", size = 0.8) +
    geom_text(aes(label = sprintf("β=%.4f\n(SE=%.4f)", estimate, std.error)),
              vjust = -0.8, size = 3) +
    coord_flip() +
    labs(title    = "DiD Coefficient Estimates: Suitability × Post",
         subtitle  = "Effect of 1pp increase in 2010 suitability on 2010–2022 outcome change",
         x = NULL, y = "Estimated Coefficient (95% CI)",
         caption = caption_both)

} else {
  cat(
    "ℹ️  DiD specification skipped: fewer than 4 districts have a valid 2010 suitability index.\n",
    "   See the diagnostic output in Section 4 to identify and fix the coding issue.\n",
    "   The first-differences results above remain valid and are the primary estimates.\n"
  )
}
```

## Interpretation

The coefficient $\hat{\beta}$ on `Suitability (2010) × Post` (DiD) or on `2010 Suitability Index` (first-differences) captures the differential change in each outcome for districts with higher pre-treatment hosting capacity. Expected signs under the STR displacement hypothesis:

| Outcome | Expected sign | Interpretation |
|----|----|----|
| Δ Rental share | **Negative** | STRs absorb long-term rental stock |
| Δ Homeownership | **Negative** | Investors convert owner-occupied homes |
| Δ Overcrowding | **Positive** | Displaced residents crowd into remaining units |

::: callout-warning
**Power caveat:** With 12 districts and 2 time periods, standard errors are large and confidence intervals wide. Treat these as directionally informative, not precise causal estimates. The constituency-level replication in @sec-constituency uses \~17 units and improves power modestly.
:::

## Scatter: Suitability vs Outcome Changes

```{r scatter-fd}
First_diff |>
  filter(!is.na(suitability_2010)) |>
  pivot_longer(
    cols      = c(d_rental_share, d_homeownership_rate, d_overcrowding_rate),
    names_to  = "outcome",
    values_to = "change"
  ) |>
  mutate(outcome = recode(outcome,
    "d_rental_share"       = "Δ Rental Share",
    "d_homeownership_rate" = "Δ Homeownership Rate",
    "d_overcrowding_rate"  = "Δ Overcrowding Rate"
  )) |>
  filter(!is.na(change)) |>
  ggplot(aes(x = suitability_2010, y = change, label = district)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(color = "#2C7BB6", size = 2.5) +
  geom_smooth(method = "lm", se = TRUE, color = "#D7191C", linewidth = 0.8) +
  geom_text_repel(size = 2.5, max.overlaps = 10) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  facet_wrap(~ outcome, scales = "free_y") +
  labs(
    title    = "2010 Hosting Suitability vs Change in Housing Outcomes (2010–2022)",
    subtitle  = "Each point = one district. Red line = weighted OLS fit.",
    x        = "2010 Hosting Suitability Index",
    y        = "Change 2010 → 2022",
    caption  = caption_both
  )

# Always show the outcome changes even if suitability is NA
First_diff |>
  select(district, d_rental_share, d_homeownership_rate, d_overcrowding_rate) |>
  pivot_longer(
    cols      = c(d_rental_share, d_homeownership_rate, d_overcrowding_rate),
    names_to  = "outcome",
    values_to = "change"
  ) |>
  mutate(outcome = recode(outcome,
    "d_rental_share"       = "Δ Rental Share",
    "d_homeownership_rate" = "Δ Homeownership Rate",
    "d_overcrowding_rate"  = "Δ Overcrowding Rate"
  )) |>
  filter(!is.na(change)) |>
  ggplot(aes(x = reorder(district, change), y = change, fill = change > 0)) +
  geom_col(show.legend = FALSE) +
  geom_hline(yintercept = 0, linewidth = 0.4) +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(values = c("#D7191C", "#2C7BB6")) +
  coord_flip() +
  facet_wrap(~ outcome, scales = "free_x") +
  labs(
    title   = "Change in Housing Outcomes by District: 2010 → 2022",
    subtitle = "Blue = increase, Red = decrease",
    x = NULL, y = "Change (pp)", caption = caption_both
  )
```

------------------------------------------------------------------------

# Constituency-Level Analysis {#sec-constituency}

Given the small number of districts (n=12), moving to the constituency level increases the number of units to approximately 17 and modestly improves statistical power. This section replicates the district-level analysis at the constituency level using the `CONSTITUENCY` / `poldist` variable.

```{r constituency-panel}
# --- 2010 constituency summaries ---
Const_2010 <- Thesis_Working_Data_2010 |>
  group_by(constituency) |>
  summarise(
    rental_share       = weighted.mean(long_term_rental,  household_weight, na.rm = TRUE),
    homeownership_rate = weighted.mean(owner_occupied,    household_weight, na.rm = TRUE),
    overcrowding_rate  = weighted.mean(overcrowded,       household_weight, na.rm = TRUE),
    suitability_index  = weighted.mean(hosting_suitable,  household_weight, na.rm = TRUE),
    total_households   = sum(household_weight, na.rm = TRUE),
    census_year        = 2010L,
    .groups = "drop"
  ) |>
  filter(!is.na(constituency))

# --- 2022 constituency summaries ---
Const_2022 <- Thesis_Working_Data_2022 |>
  group_by(constituency) |>
  summarise(
    rental_share       = weighted.mean(long_term_rental,  household_weight, na.rm = TRUE),
    homeownership_rate = weighted.mean(owner_occupied,    household_weight, na.rm = TRUE),
    overcrowding_rate  = weighted.mean(overcrowded,       household_weight, na.rm = TRUE),
    suitability_index  = weighted.mean(hosting_suitable,  household_weight, na.rm = TRUE),
    total_households   = sum(household_weight, na.rm = TRUE),
    census_year        = 2022L,
    .groups = "drop"
  ) |>
  filter(!is.na(constituency))

# Build constituency panel with 2010 suitability as treatment intensity
Const_Panel <- bind_rows(Const_2010, Const_2022) |>
  arrange(constituency, census_year) |>
  left_join(
    Const_2010 |> select(constituency, suitability_2010 = suitability_index),
    by = "constituency"
  ) |>
  mutate(post = if_else(census_year == 2022L, 1L, 0L))

# --- DiD regressions at constituency level ---
cm_rental <- feols(
  rental_share       ~ suitability_2010:post | constituency + census_year,
  data    = Const_Panel |> filter(!is.na(suitability_2010)),
  weights = ~ total_households
)
cm_own <- feols(
  homeownership_rate ~ suitability_2010:post | constituency + census_year,
  data    = Const_Panel |> filter(!is.na(suitability_2010)),
  weights = ~ total_households
)
cm_crowd <- feols(
  overcrowding_rate  ~ suitability_2010:post | constituency + census_year,
  data    = Const_Panel |> filter(!is.na(suitability_2010) & !is.na(overcrowding_rate)),
  weights = ~ total_households
)

modelsummary(
  list(
    "Rental Share"       = cm_rental,
    "Homeownership Rate" = cm_own,
    "Overcrowding Rate"  = cm_crowd
  ),
  coef_rename = c("suitability_2010:post" = "Suitability (2010) × Post"),
  stars   = c("*" = 0.10, "**" = 0.05, "***" = 0.01),
  gof_map = c("nobs", "r.squared", "FE: constituency", "FE: census_year"),
  title   = "Constituency-Level DiD Estimates (Robustness Check)",
  notes   = c(
    "Constituency and year fixed effects included.",
    "Weighted by constituency total households.",
    "* p<0.10, ** p<0.05, *** p<0.01"
  )
)
```

------------------------------------------------------------------------

# Potential Treatments

## Technology Shock: STR Platform Expansion (\~2014)

The global rollout of Airbnb and similar platforms after roughly 2014 represents a quasi-natural experiment: the technology became available nationwide at approximately the same time, but housing suitability varied pre-existing across districts. Districts with more suitable housing stock in 2010 were better positioned to adopt STR listing, creating differential exposure to the platform shock.

**Treatment intensity:** 2010 Hosting Suitability Index (used in regressions above).

**Predicted sign:** Higher suitability → larger post-2014 rental share decline, homeownership decline, and crowding increase.

## Tourism Demand Shock: International Airlift Expansion (\~2015–2019)

New international routes to Saint Lucia increased tourist arrivals, raising demand for accommodation. Districts near tourism infrastructure (beaches, resort zones) would experience stronger demand shocks.

**Treatment intensity (alternative):** Distance to Hewanorra International Airport (southern routes) or George F. L. Charles Airport (northern/Caribbean routes), interacted with post-period.

**Note:** This treatment cannot be fully separated from the platform expansion channel with the available data. A robustness check would require flight-level data by destination airport.

## Housing Supply Shock: Investment Incentives (2014–2015)

The Tourism Stimulus and Investment Act (2014) and Citizenship by Investment Act (2015) subsidised tourism-related real estate development. These may have shifted housing supply toward short-term or luxury use, displacing long-term residents.

**Treatment intensity (alternative):** A binary indicator for districts containing approved real estate investment projects, from the Citizenship by Investment Unit project registry.

------------------------------------------------------------------------

# Contingency Plan

If the `dwell_status` variable cannot be obtained from the Saint Lucia Central Statistics Office before the project deadline, the analysis is reframed around housing outcomes already in both censuses: **average monthly rent** and **homeownership rates** by district, supplemented by the crowding indicators already computed.

The 2010 hosting suitability index serves as the instrument for STR adoption intensity. The exclusion restriction requires that the 2010 suitability index (spare bedrooms, piped water, electricity, sanitation) affects post-2014 housing market outcomes *only through* STR adoption, not through other channels. This is plausible because these are physical housing stock characteristics determined well before the platform era, and there is no strong reason to expect them to directly predict 2022 rent or ownership rates except through the STR channel.

If the district-level sample proves too small for reliable estimation, the constituency-level replication in @sec-constituency provides the primary robustness check. As a second fallback, the paper can be framed as a prospective research design: documenting pre-treatment conditions, validating the instrument, and establishing the expected causal channels, with an explicit invitation for future researchers to complete the analysis when STR data become available.

------------------------------------------------------------------------

## Parallel Trends: Visual Check

With only two time periods, a formal pre-trends test is impossible. However, the following plot shows the cross-district correlation between 2010 suitability and baseline (2010) housing outcomes. If high-suitability districts were already on systematically different levels *before* the platform expansion, the DiD assumption would be more tenuous.

```{r parallel-trends}
# Check: does 2010 suitability predict 2010 levels of outcomes?
# If yes, the fixed effects absorb this — but the pattern is informative
Panel_2010 |>
  filter(!is.na(suitability_index)) |>
  pivot_longer(c(rental_share, homeownership_rate, overcrowding_rate),
               names_to = "outcome", values_to = "value_2010") |>
  filter(!is.na(value_2010)) |>
  mutate(outcome = recode(outcome,
    "rental_share"       = "Rental Share (2010)",
    "homeownership_rate" = "Homeownership Rate (2010)",
    "overcrowding_rate"  = "Overcrowding Rate (2010)"
  )) |>
  ggplot(aes(x = suitability_index, y = value_2010, label = district)) +
  geom_point(color = "#2C7BB6", size = 2.5) +
  geom_smooth(method = "lm", se = TRUE, color = "#D7191C", linewidth = 0.8) +
  geom_text_repel(size = 2.5) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  facet_wrap(~ outcome, scales = "free_y") +
  labs(
    title   = "2010 Suitability vs 2010 Baseline Outcomes",
    subtitle = "Checks whether high-suitability districts already differed pre-treatment",
    x       = "2010 Hosting Suitability Index",
    y       = "2010 Outcome Level",
    caption = caption_2010
  )
```

------------------------------------------------------------------------

# Session Info

```{r session}
sessionInfo()
```
