---
title: "Dataset Variable Overview"
subtitle: "2012 and 2022 Population & Housing Census — Merged Person-Household Files"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Contents"
    theme: cosmo
    code-fold: true
    self-contained: true
    df-print: kable
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(haven)
library(dplyr)
library(knitr)
library(kableExtra)

df2012 <- read_sav("person_house_merged.sav")
df2022 <- read_sav("PersonHHoldMerge 2022 Annon.sav")

get_labels <- function(df) {
  data.frame(
    `#` = seq_len(ncol(df)),
    Variable = names(df),
    Label = sapply(df, function(x) {
      lbl <- attr(x, "label")
      if (is.null(lbl) || lbl == "") "—" else as.character(lbl)
    }),
    Type = sapply(df, function(x) {
      cl <- class(x)[1]
      if (cl == "haven_labelled") "Labelled"
      else if (cl == "numeric") "Numeric"
      else if (cl == "character") "Character"
      else cl
    }),
    check.names = FALSE,
    stringsAsFactors = FALSE,
    row.names = NULL
  )
}

vars2012 <- get_labels(df2012)
vars2022 <- get_labels(df2022)

make_table <- function(df) {
  kable(df, align = c("r", "l", "l", "l")) |>
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed", "responsive"),
      full_width = TRUE,
      font_size = 13
    ) |>
    column_spec(1, width = "3em", bold = FALSE, color = "grey") |>
    column_spec(2, bold = TRUE, monospace = TRUE) |>
    column_spec(3, width = "45%") |>
    column_spec(4, width = "10em")
}
```

## Summary

| | 2012 Dataset | 2022 Dataset |
|---|---|---|
| **File** | `person_house_merged.sav` | `PersonHHoldMerge 2022 Annon.sav` |
| **Total Variables** | `r ncol(df2012)` | `r ncol(df2022)` |
| **Total Records** | `r format(nrow(df2012), big.mark=",")` | `r format(nrow(df2022), big.mark=",")` |

---

## 2012 Dataset Variables

**File:** `person_house_merged.sav` — **`r ncol(df2012)` variables**, **`r format(nrow(df2012), big.mark=",")`** records

```{r}
make_table(vars2012)
```

---

## 2022 Dataset Variables

**File:** `PersonHHoldMerge 2022 Annon.sav` — **`r ncol(df2022)` variables**, **`r format(nrow(df2022), big.mark=",")`** records

```{r}
make_table(vars2022)
```

---

## Variables in Both Datasets

Variables whose names appear in both files (exact match, case-sensitive).

```{r}
common <- intersect(names(df2012), names(df2022))
if (length(common) == 0) {
  cat("No exact-match variable names shared between the two datasets.")
} else {
  data.frame(Variable = common) |>
    mutate(
      `Label (2012)` = sapply(common, function(v) {
        lbl <- attr(df2012[[v]], "label")
        if (is.null(lbl) || lbl == "") "—" else as.character(lbl)
      }),
      `Label (2022)` = sapply(common, function(v) {
        lbl <- attr(df2022[[v]], "label")
        if (is.null(lbl) || lbl == "") "—" else as.character(lbl)
      })
    ) |>
    kable(align = c("l", "l", "l")) |>
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed", "responsive"),
      full_width = TRUE,
      font_size = 13
    ) |>
    column_spec(1, bold = TRUE, monospace = TRUE)
}
```

---

## Variables Only in 2012

```{r}
only2012 <- setdiff(names(df2012), names(df2022))
vars2012 |>
  filter(Variable %in% only2012) |>
  select(-`#`) |>
  mutate(`#` = seq_len(n())) |>
  select(`#`, everything()) |>
  make_table()
```

---

## Variables Only in 2022

```{r}
only2022 <- setdiff(names(df2022), names(df2012))
vars2022 |>
  filter(Variable %in% only2022) |>
  select(-`#`) |>
  mutate(`#` = seq_len(n())) |>
  select(`#`, everything()) |>
  make_table()
```
